---
title: "Model evaluations"
author: "Zuofu Huang"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse); library(ggplot2); library(lubridate); library(TraMineR); library(performance)
library(GLMMadaptive); library(pscl); library(gridExtra); library(MASS)
library(clValid); library(clv); library(TraMineRextras); library(simukde)
```


```{r}
# "baseline" sequence
sequences <- read.csv("../Data in use/original_seqs.csv")[,-1]
```


```{r}
# TVMC on original sequences
cluster_TVMC <- read.csv("../Data in use/sim_seqs_cluster_TVMC.csv")[,-1]
noCluster_TVMC <- read.csv("../Data in use/sim_seqs_noCluster_TVMC.csv")[,-1]
```


```{r}
# "basic" synthesis on original sequences (cluster/no cluster + order 1/2)
cluster <- read.csv("../Data in use/sim_seqs_cluster.csv")[,-1]
noCluster <- read.csv("../Data in use/sim_seqs_noCluster.csv")[,-1]

cluster_order2 <- read.csv("../Data in use/sim_seqs_cluster_order2.csv")[,-1]
noCluster_order2 <- read.csv("../Data in use/sim_seqs_noCluster_order2.csv")[,-1]
```


```{r}
# "basic" synthesis on imputed sequences (cluster/no cluster + order 1/2)
imputed_cluster <- read.csv("../Data in use/sim_seqs_imputed_cluster.csv")[,2:1441]
imputed_noCluster <- read.csv("../Data in use/sim_seqs_imputed_noCluster.csv")[,2:1441]

imputed_cluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_cluster_order2.csv")[,2:1441]
imputed_noCluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_order2.csv")[,2:1441]
```




```{r}
# KDE synthesis on imputed sequences (cluster/no cluster + order 1/2)
imputed_KDE_cluster <- read.csv("../Data in use/sim_seqs_imputed_KDE_cluster.csv")[,2:1441]
imputed_KDE_noCluster <- read.csv("../Data in use/sim_seqs_imputed_KDE_noCluster.csv")[,2:1441]

imputed_KDE_cluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_KDE_cluster_order2.csv")[,2:1441]
imputed_KDE_noCluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_KDE_noCluster_order2.csv")[,2:1441]
```


```{r}
# logspline
imputed_log_cluster <- read.csv("../Data in use/sim_seqs_imputed_log_cluster.csv")[,2:1441]
imputed_log_noCluster <- read.csv("../Data in use/sim_seqs_imputed_log_noCluster.csv")[,2:1441]

imputed_log_cluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_log_cluster_order2.csv")[,2:1441]
imputed_log_noCluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_log_noCluster_order2.csv")[,2:1441]
```


```{r}
# Investigate effect of time window (30min/60min/120min) on imputed KDE sequences
imputed_cluster_30 <- read.csv("../Data in use/sim_seqs_imputed_cluster_30min.csv")[,2:1441]
# imputed_noCluster_30 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_30min.csv")[,2:1441]
# 
imputed_cluster_120 <- read.csv("../Data in use/sim_seqs_imputed_cluster_120min.csv")[,2:1441]
# imputed_noCluster_120 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_120min.csv")[,2:1441]
# 
imputed_cluster_order2_30 <- read.csv("../Data in use/sim_seqs_imputed_cluster_order2_30min.csv")[,2:1441]
# imputed_noCluster_order2_30 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_order2_30min.csv")[,2:1441]
# 
imputed_cluster_order2_120 <- read.csv("../Data in use/sim_seqs_imputed_cluster_order2_120min.csv")[,2:1441]
# imputed_noCluster_order2_120 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_order2_120min.csv")[,2:1441]
```


## Create TramineR objects

```{r message=FALSE, warning=FALSE}
# "baseline" sequences
sequences_T <- seqdef(sequences)
```


```{r message=FALSE, warning=FALSE}
# TVMC on original sequences
cluster_TVMC_T <- seqdef(cluster_TVMC)
noCluster_TVMC_T <- seqdef(noCluster_TVMC)
```


```{r message=FALSE, warning=FALSE}
# "basic" synthesis on original sequences (cluster/no cluster + order 1/2)
cluster_T <- seqdef(cluster)
noCluster_T <- seqdef(noCluster)

cluster_order2_T <- seqdef(cluster_order2)
noCluster_order2_T <- seqdef(noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# "basic" synthesis on imputed sequences (cluster/no cluster + order 1/2)
imputed_cluster_T <- seqdef(imputed_cluster)
imputed_noCluster_T <- seqdef(imputed_noCluster)

imputed_cluster_order2_T <- seqdef(imputed_cluster_order2)
imputed_noCluster_order2_T <- seqdef(imputed_noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# KDE synthesis on imputed sequences (cluster/no cluster + order 1/2)
imputed_KDE_cluster_T <- seqdef(imputed_KDE_cluster)
imputed_KDE_noCluster_T <- seqdef(imputed_KDE_noCluster)

imputed_KDE_cluster_order2_T <- seqdef(imputed_KDE_cluster_order2)
imputed_KDE_noCluster_order2_T <- seqdef(imputed_KDE_noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# logspline on imputed sequences (cluster/no cluster + order 1/2)
imputed_log_cluster_T <- seqdef(imputed_log_cluster)
imputed_log_noCluster_T <- seqdef(imputed_log_noCluster)

imputed_log_cluster_order2_T <- seqdef(imputed_log_cluster_order2)
imputed_log_noCluster_order2_T <- seqdef(imputed_log_noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# Investigate effect of time window (30min/60min/120min) on imputed sequences
imputed_cluster_30_T <- seqdef(imputed_cluster_30)
# imputed_noCluster_30_T <- seqdef(imputed_noCluster_30)
# 
imputed_cluster_120_T <- seqdef(imputed_cluster_120)
# imputed_noCluster_120_T <- seqdef(imputed_noCluster_120)
# 
imputed_cluster_order2_30_T <- seqdef(imputed_cluster_order2_30)
# imputed_noCluster_order2_30_T <- seqdef(imputed_noCluster_order2_30)
# 
imputed_cluster_order2_120_T <- seqdef(imputed_cluster_order2_120)
# imputed_noCluster_order2_120_T <- seqdef(imputed_noCluster_order2_120)
```


```{r}
# sim_list <- list(sequences, cluster_TVMC, noCluster_TVMC, cluster, noCluster, cluster_order2, noCluster_order2, imputed_cluster, imputed_noCluster, imputed_cluster_order2, imputed_noCluster_order2, imputed_KDE_cluster, imputed_KDE_noCluster, imputed_KDE_cluster_order2, imputed_KDE_noCluster_order2, imputed_log_cluster, imputed_log_noCluster, imputed_log_cluster_order2, imputed_log_noCluster_order2)

# sim_list_T <- list(sequences_T, cluster_TVMC_T, noCluster_TVMC_T, cluster_T, noCluster_T, cluster_order2_T, noCluster_order2_T, imputed_cluster_T, imputed_noCluster_T, imputed_cluster_order2_T, imputed_noCluster_order2_T, imputed_KDE_cluster_T, imputed_KDE_noCluster_T, imputed_KDE_cluster_order2_T, imputed_KDE_noCluster_order2_T, imputed_log_cluster_T, imputed_log_noCluster_T, imputed_log_cluster_order2_T, imputed_log_noCluster_order2_T)
```

```{r}
# sim_list <- list(sequences, cluster_TVMC, noCluster_TVMC, imputed_cluster, imputed_noCluster, imputed_cluster_order2, imputed_noCluster_order2)
# 
# sim_list_T <- list(sequences_T, cluster_TVMC_T, noCluster_TVMC_T, imputed_cluster_T, imputed_noCluster_T, imputed_cluster_order2_T, imputed_noCluster_order2_T)
```

```{r}
sim_list_window <- list(sequences, imputed_cluster, imputed_cluster_order2, imputed_cluster_30, imputed_cluster_order2_30, imputed_cluster_120, imputed_cluster_order2_120)

sim_list_window_T <- list(sequences_T, imputed_cluster_T, imputed_cluster_order2_T, imputed_cluster_30_T, imputed_cluster_order2_30_T, imputed_cluster_120_T, imputed_cluster_order2_120_T)
```


# Tool examples

## Distribution plots

```{r message=FALSE}
### Example:
# sequences[sequences == "N/A"] <- NA
# p_sequences <- seqplot(seqdef(sequences), border = NA, type = "d", cex.legend = 0.5)

# this <- as.data.frame(sim_list[[1]])
# this[this == "N/A"] <- NA
# seqplot(seqdef(this), border = NA, type = "d", cex.legend = 0.5)
```


## Percentage of each activity

```{r}
### Example:
# a_sequences <- seqmeant(sequences_T)
```


## Distribution of duration of each activity

```{r}
### Example:
dist_of_activity_dur <- function(traminer_seq){
  dist <- seqistatd(traminer_seq)
  means <- apply(dist, 2, mean)
  sds <- apply(dist, 2, sd)
  return(list(means,sds))
}

# dist1 <- seqistatd(sequences_T)
# c1 <- apply(dist1, 2, mean)
# d1 <- apply(dist1, 2, sd)
```


## The distribution of number of distinct states in each sequence

```{r}
num_of_distinct_states <- function(traminer_seq){
  return(seqlength(seqdss(traminer_seq)))
}
```


## How much work/home does each day have?

```{r}
length_of_certain_activity <- function(traminer_seq, activity){
  dist <- seqistatd(traminer_seq)
  return(dist[,activity])
}

### Example:
# work1 <- dist1[,"WORK"]
```


```{r}
# dat <- as.data.frame(cbind(c(work1, work6, work7, work8, work9, work10, work11), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Our Method",1929*2), rep("Our Method + order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))
# 
# colnames(dat) <- c("Length", "Method","Clustered")
# dat$Length <- as.numeric(dat$Length)
```


```{r}
# ggplot(data = dat, aes(x = Length)) +
#   facet_grid(Clustered ~ Method) +
#   geom_histogram(binwidth = 50) +
#   theme_bw()
```

Maybe if the clustering idea is good, we can think of adding the individual level through clustering as well.


## Number of distinct activity periods per day

```{r}
num_distinct_periods_perday <- function(traminer_seq, activity){
  return(table(rowSums(seqdss(traminer_seq) == activity)))
}

### Example:
# work_num1 <- table(rowSums(seqdss(sequences_T) == "WORK"))
```



## Sum of percentage of each state squared

```{r}
# ref and data are traminer objects
sum_of_state_pct <- function(ref, data){
  ref_prob <- seqstatd(ref)[["Frequencies"]]
  data_prob <- seqstatd(data)[["Frequencies"]]
  
  dist <- 0
  for (i in 1:ncol(ref_prob)){
    this_ref <- as.vector(ref_prob[,i])
    this_data <- as.vector(data_prob[,i])
    this_dist <- sum((this_ref - this_data)^2)
    dist <- dist + this_dist
  }
  return(dist)
}


### Example: 
# sum_of_state_pct(sequences_T, cluster_T)
```


## Entropy

```{r}
### Example:
# entropy1 <- TraMineR::seqient(sequences_T)
```


## Transition Matrix?

```{r}
# tm1 <- seqtrate(sequences_T)
# tm6 <- seqtrate(sim_seqs_cluster_TVMC_T)
# tm7 <- seqtrate(sim_seqs_noCluster_TVMC_T)
# tm8 <- seqtrate(sim_seqs_imputed_cluster_T)
# tm9 <- seqtrate(sim_seqs_imputed_noCluster_T)
# tm10 <- seqtrate(sim_seqs_imputed_cluster_order2_T)
# tm11 <- seqtrate(sim_seqs_imputed_noCluster_order2_T)
```

```{r}
# heatmap(tm1 - tm6, Rowv = NA, Colv = NA)
# heatmap(tm1 - tm7, Rowv = NA, Colv = NA)
# heatmap(tm1 - tm8, Rowv = NA, Colv = NA)
# heatmap(tm1 - tm9, Rowv = NA, Colv = NA)
# heatmap(tm1 - tm10, Rowv = NA, Colv = NA)
# heatmap(tm1 - tm11, Rowv = NA, Colv = NA)
```


## Durations of each state (to show that they are not exponentially distributed)

```{r}
# find_lengths <- function(seq, state){
#   rled <- rle(seq)
#   lengths <- rled$lengths[which(rled$values == state)]
#   return(lengths)
# }
# 
# works <- unlist(apply(sequences, 1, find_lengths, state = "WORK"))
# homes <- unlist(apply(sequences, 1, find_lengths, state = "HOME"))
# cars <- unlist(apply(sequences, 1, find_lengths, state = "CAR"))
# 
# g1 <- ggplot(data = data.frame(works), aes(x = works)) + 
#   geom_density() +
#   scale_x_continuous(limits = c(0, 1440)) +
#   theme_bw() + 
#   xlab("Duration of work episodes") + 
#   ggtitle("Distribution of work episodes")
# 
# g2 <- ggplot(data = data.frame(homes), aes(x = homes)) + 
#   geom_density() +
#   scale_x_continuous(limits = c(0, 1440)) +
#   theme_bw() + 
#   xlab("Duration of home episodes") + 
#   ggtitle("Distribution of home episodes")
# 
# g3 <- ggplot(data = data.frame(cars), aes(x = cars)) + 
#   geom_density() + 
#   scale_x_continuous(limits = c(0, 1440)) +
#   theme_bw() + 
#   xlab("Duration of car episodes") + 
#   ggtitle("Distribution of car episodes")
#   
# 
# grid.arrange(g1,g2,g3, nrow = 3)
```






<!-- # Main comparisons -->

<!-- Evaluation criteria: -->

<!-- 1. Transition matrix and heatmap? (TO BE DEVELOPED) -->

<!-- 2. Distribution of state durations (Mean and SD of each activity) -->

<!-- 3. Distribution of number of distinct states (Mean and SD) -->

<!-- 4. Distribution of entropies (and K-S test statistic p-value against original sequences) -->

<!-- 5. Distribution of daily hours spent on work/home states (and K-S test statistic p-value against original sequences) -->




<!-- 2. Distribution of state durations (Mean and SD of each activity) -->

<!-- ```{r} -->
<!-- this <- lapply(sim_list_T, dist_of_activity_dur) -->
<!-- means <- as.matrix(sapply(this,"[[", 1)) -->
<!-- means_prop <- means -->

<!-- for (i in 2:7){ -->
<!--   for (j in 1:13){ -->
<!--     means_prop[j,i] <- paste0(round((means[j,i]/means[j,1] - 1) * 100,1), "%") -->
<!--   } -->
<!-- } -->
<!-- means <- round(means, 2) -->
<!-- means_prop[,1] <- round(as.vector(as.numeric((means_prop[,1]), 2)), 2) -->



<!-- sds <- as.matrix(sapply(this,"[[", 2)) -->
<!-- sds_prop <- sds -->

<!-- for (i in 2:7){ -->
<!--   for (j in 1:13){ -->
<!--     sds_prop[j,i] <- paste0(round((sds[j,i]/sds[j,1] - 1) * 100,1), "%") -->
<!--   } -->
<!-- } -->
<!-- sds <- round(sds, 2) -->
<!-- sds_prop[,1] <- round(as.vector(as.numeric((sds_prop[,1]), 2)), 2) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # result <- means -->
<!-- #  -->
<!-- # for(i in 1:nrow(means)){ -->
<!-- #   for (j in 1:ncol(means)){ -->
<!-- #     result[i,j] <- paste0(means[i,j], " (", sds[i,j],")") -->
<!-- #   } -->
<!-- # } -->
<!-- ``` -->



<!-- 3. Distribution of number of distinct states (Mean and SD) -->

<!-- ```{r} -->
<!-- dists <- lapply(sim_list_T, num_of_distinct_states) -->

<!-- means <- sapply(dists, mean) -->
<!-- round(means, 2) -->
<!-- sds <- sapply(dists, sd) -->
<!-- round(sds, 2) -->
<!-- ``` -->


<!-- 4. Distribution of entropies (and K-S test statistic p-value against original sequences) -->

<!-- ```{r} -->
<!-- entropies <- lapply(sim_list_T, TraMineR::seqient) -->

<!-- pvalues <- c() -->
<!-- for (i in 2:7){ -->
<!--   pvalues <- c(pvalues, ks.test(entropies[[1]], entropies[[i]])$p.value) -->
<!-- } -->

<!-- pvalues -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Consider plots -->
<!-- entropy_dat <- as.data.frame(cbind(c(entropies[[1]], entropies[[2]], entropies[[3]], entropies[[4]], entropies[[5]], entropies[[6]], entropies[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929)))) -->

<!-- colnames(entropy_dat) <- c("Length", "Method", "Clustered") -->
<!-- entropy_dat$Length <- as.numeric(entropy_dat$Length) -->
<!-- entropy_dat$Method <- factor(entropy_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2")) -->

<!-- ggplot(data = entropy_dat, aes(x = Length)) + -->
<!--   facet_grid(Clustered ~ Method) + -->
<!--   geom_histogram(binwidth = 0.02) + -->
<!--   theme_bw() -->
<!-- ``` -->


<!-- ## 5. Distribution of daily hours spent on work/home states (and K-S test statistic p-value against original sequences) -->

<!-- ### **WORK** -->

<!-- ```{r} -->
<!-- dists <- lapply(sim_list_T, length_of_certain_activity, activity = "WORK") -->

<!-- pvalues_work <- c() -->
<!-- for (i in 2:7){ -->
<!--   pvalues_work <- c(pvalues_work, ks.test(dists[[1]], dists[[i]])$p.value) -->
<!-- } -->

<!-- pvalues_work -->

<!-- work_dist_dat <- as.data.frame(cbind(c(dists[[1]], dists[[2]], dists[[3]], dists[[4]], dists[[5]], dists[[6]], dists[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929)))) -->

<!-- colnames(work_dist_dat) <- c("Length", "Method", "Clustered") -->
<!-- work_dist_dat$Length <- as.numeric(work_dist_dat$Length) -->
<!-- work_dist_dat$Method <- factor(work_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2")) -->

<!-- ggplot(data = work_dist_dat, aes(x = Length)) + -->
<!--   facet_grid(Clustered ~ Method) + -->
<!--   geom_histogram(binwidth = 30) + -->
<!--   theme_bw() -->

<!-- ggplot(data = work_dist_dat[work_dist_dat$Length != 0,], aes(x = Length)) + -->
<!--   facet_grid(Clustered ~ Method) + -->
<!--   geom_histogram(binwidth = 30) + -->
<!--   theme_bw() -->
<!-- ``` -->




<!-- ### **HOME** -->

<!-- ```{r} -->
<!-- dists_home <- lapply(sim_list_T, length_of_certain_activity, activity = "HOME") -->

<!-- pvalues_home <- c() -->
<!-- for (i in 2:7){ -->
<!--   pvalues_home <- c(pvalues_home, ks.test(dists_home[[1]], dists_home[[i]])$p.value) -->
<!-- } -->

<!-- pvalues_home -->

<!-- home_dist_dat <- as.data.frame(cbind(c(dists_home[[1]], dists_home[[2]], dists_home[[3]], dists_home[[4]], dists_home[[5]], dists_home[[6]], dists_home[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929)))) -->

<!-- colnames(home_dist_dat) <- c("Length", "Method", "Clustered") -->
<!-- home_dist_dat$Length <- as.numeric(home_dist_dat$Length) -->
<!-- home_dist_dat$Method <- factor(home_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2")) -->

<!-- ggplot(data = home_dist_dat, aes(x = Length)) + -->
<!--   facet_grid(Clustered ~ Method) + -->
<!--   geom_histogram(binwidth = 30) + -->
<!--   theme_bw() -->

<!-- ggplot(data = home_dist_dat[home_dist_dat$Length != 1440,], aes(x = Length)) + -->
<!--   facet_grid(Clustered ~ Method) + -->
<!--   geom_histogram(binwidth = 30) + -->
<!--   theme_bw() -->
<!-- ``` -->



<!-- ### **car** -->

<!-- ```{r} -->
<!-- dists_car <- lapply(sim_list_T, length_of_certain_activity, activity = "CAR") -->

<!-- pvalues_car <- c() -->
<!-- for (i in 2:7){ -->
<!--   pvalues_car <- c(pvalues_car, ks.test(dists_car[[1]], dists_car[[i]])$p.value) -->
<!-- } -->

<!-- pvalues_car -->

<!-- car_dist_dat <- as.data.frame(cbind(c(dists_car[[1]], dists_car[[2]], dists_car[[3]], dists_car[[4]], dists_car[[5]], dists_car[[6]], dists_car[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929)))) -->

<!-- colnames(car_dist_dat) <- c("Length", "Method", "Clustered") -->
<!-- car_dist_dat$Length <- as.numeric(car_dist_dat$Length) -->
<!-- car_dist_dat$Method <- factor(car_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2")) -->

<!-- ggplot(data = car_dist_dat, aes(x = Length)) + -->
<!--   facet_grid(Clustered ~ Method) + -->
<!--   geom_histogram(binwidth = 5) + -->
<!--   theme_bw() -->
<!-- ``` -->


<!-- ### **Leisure and recreation** -->

<!-- ```{r} -->
<!-- dists_LR <- lapply(sim_list_T, length_of_certain_activity, activity = "LEISURE_RECREATION") -->

<!-- pvalues_LR <- c() -->
<!-- for (i in 2:7){ -->
<!--   pvalues_LR <- c(pvalues_LR, ks.test(dists_LR[[1]], dists_LR[[i]])$p.value) -->
<!-- } -->

<!-- pvalues_LR -->

<!-- LR_dist_dat <- as.data.frame(cbind(c(dists_LR[[1]], dists_LR[[2]], dists_LR[[3]], dists_LR[[4]], dists_LR[[5]], dists_LR[[6]], dists_LR[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929)))) -->

<!-- colnames(LR_dist_dat) <- c("Length", "Method", "Clustered") -->
<!-- LR_dist_dat$Length <- as.numeric(LR_dist_dat$Length) -->
<!-- LR_dist_dat$Method <- factor(LR_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2")) -->
<!-- # -->
<!-- # ggplot(data = LR_dist_dat, aes(x = Length)) + -->
<!-- #   facet_grid(Clustered ~ Method) + -->
<!-- #   geom_histogram(binwidth = 30) + -->
<!-- #   theme_bw() -->

<!-- ggplot(data = LR_dist_dat[LR_dist_dat$Length != 0,], aes(x = Length)) + -->
<!--   facet_grid(Clustered ~ Method) + -->
<!--   geom_histogram(binwidth = 20) + -->
<!--   theme_bw() -->
<!-- ``` -->


<!-- ### **Personal Business** -->


<!-- ```{r} -->
<!-- dists_PB <- lapply(sim_list_T, length_of_certain_activity, activity = "PERSONAL_BUSINESS") -->

<!-- pvalues_PB <- c() -->
<!-- for (i in 2:7){ -->
<!--   pvalues_PB <- c(pvalues_PB, ks.test(dists_PB[[1]], dists_PB[[i]])$p.value) -->
<!-- } -->

<!-- pvalues_PB -->

<!-- PB_dist_dat <- as.data.frame(cbind(c(dists_PB[[1]], dists_PB[[2]], dists_PB[[3]], dists_PB[[4]], dists_PB[[5]], dists_PB[[6]], dists_PB[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929)))) -->

<!-- colnames(PB_dist_dat) <- c("Length", "Method", "Clustered") -->
<!-- PB_dist_dat$Length <- as.numeric(PB_dist_dat$Length) -->
<!-- PB_dist_dat$Method <- factor(PB_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2")) -->

<!-- ggplot(data = PB_dist_dat[PB_dist_dat$Length != 0,], aes(x = Length)) + -->
<!--   facet_grid(Clustered ~ Method) + -->
<!--   geom_histogram(binwidth = 20) + -->
<!--   theme_bw() -->
<!-- ``` -->



<!-- ## Others: -->

<!-- Sum of percentage of each state at each time squared -->

<!-- ```{r} -->
<!-- sapply(sim_list_T, sum_of_state_pct, ref = sequences_T) -->
<!-- ``` -->



<!-- ```{r} -->
<!-- num_distinct_periods_perday(sim_list_T[[19]], "WORK") -->
<!-- ``` -->





# Time window

## 2. Distribution of state durations (Mean and SD of each activity)


```{r}
this <- lapply(sim_list_window_T, dist_of_activity_dur)
means <- as.matrix(sapply(this,"[[", 1))
means_prop <- means

for (i in 2:7){
  for (j in 1:13){
    means_prop[j,i] <- paste0(round((means[j,i]/means[j,1] - 1) * 100,1), "%")
  }
}
means <- round(means, 2)
means_prop[,1] <- round(as.vector(as.numeric((means_prop[,1]), 2)), 2)



sds <- as.matrix(sapply(this,"[[", 2))
sds_prop <- sds

for (i in 2:7){
  for (j in 1:13){
    sds_prop[j,i] <- paste0(round((sds[j,i]/sds[j,1] - 1) * 100,1), "%")
  }
}
sds <- round(sds, 2)
sds_prop[,1] <- round(as.vector(as.numeric((sds_prop[,1]), 2)), 2)
```



## 3. Distribution of number of distinct states (Mean and SD)

```{r}
dists <- lapply(sim_list_window_T, num_of_distinct_states)

means <- sapply(dists, mean)
round(means, 2)
sds <- sapply(dists, sd)
round(sds, 2)
```


## 4. Distribution of entropies (and K-S test statistic p-value against original sequences)

```{r}
entropies <- lapply(sim_list_window_T, TraMineR::seqient)

pvalues <- c()
for (i in 2:7){
  pvalues <- c(pvalues, ks.test(entropies[[1]], entropies[[i]])$p.value)
}

pvalues
```

```{r}
# Consider plots
entropy_dat <- as.data.frame(cbind(c(entropies[[1]], entropies[[2]], entropies[[3]], entropies[[4]], entropies[[5]], entropies[[6]], entropies[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(entropy_dat) <- c("Length", "Time_window", "Order")
entropy_dat$Length <- as.numeric(entropy_dat$Length)
entropy_dat$Time_window <- factor(entropy_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

ggplot(data = entropy_dat, aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 0.02) +
  theme_bw()
```


## 5. Distribution of daily hours spent on work/home states (and K-S test statistic p-value against original sequences)

### **WORK**

```{r}
dists <- lapply(sim_list_window_T, length_of_certain_activity, activity = "WORK")

pvalues_work <- c()
for (i in 2:7){
  pvalues_work <- c(pvalues_work, ks.test(dists[[1]], dists[[i]])$p.value)
}

pvalues_work

work_dist_dat <- as.data.frame(cbind(c(dists[[1]], dists[[2]], dists[[3]], dists[[4]], dists[[5]], dists[[6]], dists[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(work_dist_dat) <- c("Length", "Time_window", "Order")
work_dist_dat$Length <- as.numeric(work_dist_dat$Length)
work_dist_dat$Time_window <- factor(work_dist_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

ggplot(data = work_dist_dat, aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()

ggplot(data = work_dist_dat[work_dist_dat$Length != 0,], aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```


### **HOME**

```{r}
dists_home <- lapply(sim_list_window_T, length_of_certain_activity, activity = "HOME")

pvalues_home <- c()
for (i in 2:7){
  pvalues_home <- c(pvalues_home, ks.test(dists_home[[1]], dists_home[[i]])$p.value)
}

pvalues_home

home_dist_dat <- as.data.frame(cbind(c(dists_home[[1]], dists_home[[2]], dists_home[[3]], dists_home[[4]], dists_home[[5]], dists_home[[6]], dists_home[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(home_dist_dat) <- c("Length", "Time_window", "Order")
home_dist_dat$Length <- as.numeric(home_dist_dat$Length)
home_dist_dat$Time_window <- factor(home_dist_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

ggplot(data = home_dist_dat, aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()

ggplot(data = home_dist_dat[home_dist_dat$Length != 1440,], aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```




### **CAR**

```{r}
dists_car <- lapply(sim_list_window_T, length_of_certain_activity, activity = "CAR")

pvalues_car <- c()
for (i in 2:7){
  pvalues_car <- c(pvalues_car, ks.test(dists_car[[1]], dists_car[[i]])$p.value)
}

pvalues_car

car_dist_dat <- as.data.frame(cbind(c(dists_car[[1]], dists_car[[2]], dists_car[[3]], dists_car[[4]], dists_car[[5]], dists_car[[6]], dists_car[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(car_dist_dat) <- c("Length", "Time_window", "Order")
car_dist_dat$Length <- as.numeric(car_dist_dat$Length)
car_dist_dat$Time_window <- factor(car_dist_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

ggplot(data = car_dist_dat, aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 5) +
  theme_bw()

# ggplot(data = car_dist_dat[car_dist_dat$Length < 300,], aes(x = Length)) +
#   facet_grid(Order ~ Time_window) +
#   geom_histogram(binwidth = 5) +
#   theme_bw()
```



### **LEISURE_RECREATION**

```{r}
dists_LR <- lapply(sim_list_window_T, length_of_certain_activity, activity = "LEISURE_RECREATION")

pvalues_LR <- c()
for (i in 2:7){
  pvalues_LR <- c(pvalues_LR, ks.test(dists_LR[[1]], dists_LR[[i]])$p.value)
}

pvalues_LR

LR_dist_dat <- as.data.frame(cbind(c(dists_LR[[1]], dists_LR[[2]], dists_LR[[3]], dists_LR[[4]], dists_LR[[5]], dists_LR[[6]], dists_LR[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(LR_dist_dat) <- c("Length", "Time_window", "Order")
LR_dist_dat$Length <- as.numeric(LR_dist_dat$Length)
LR_dist_dat$Time_window <- factor(LR_dist_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

# ggplot(data = LR_dist_dat, aes(x = Length)) +
#   facet_grid(Order ~ Time_window) +
#   geom_histogram(binwidth = 20) +
#   theme_bw()

ggplot(data = LR_dist_dat[LR_dist_dat$Length != 0,], aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 20) +
  theme_bw()
```


### **PERSONAL_BUSINESS**

```{r}
dists_PB <- lapply(sim_list_window_T, length_of_certain_activity, activity = "PERSONAL_BUSINESS")

pvalues_PB <- c()
for (i in 2:7){
  pvalues_PB <- c(pvalues_PB, ks.test(dists_PB[[1]], dists_PB[[i]])$p.value)
}

pvalues_PB

PB_dist_dat <- as.data.frame(cbind(c(dists_PB[[1]], dists_PB[[2]], dists_PB[[3]], dists_PB[[4]], dists_PB[[5]], dists_PB[[6]], dists_PB[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(PB_dist_dat) <- c("Length", "Time_window", "Order")
PB_dist_dat$Length <- as.numeric(PB_dist_dat$Length)
PB_dist_dat$Time_window <- factor(PB_dist_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

# ggplot(data = PB_dist_dat, aes(x = Length)) +
#   facet_grid(Order ~ Time_window) +
#   geom_histogram(binwidth = 30) +
#   theme_bw()

ggplot(data = PB_dist_dat[PB_dist_dat$Length != 0,], aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 20) +
  theme_bw()
```

## Others:

Sum of percentage of each state at each time squared

```{r}
sapply(sim_list_window_T, sum_of_state_pct, ref = sequences_T)
```


```{r}
num_distinct_periods_perday(sim_list_window_T[[1]], "WORK")
```

