---
title: "Eval 2nd data"
author: "Zuofu Huang"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse); library(ggplot2); library(lubridate); library(TraMineR); library(performance)
library(GLMMadaptive); library(pscl); library(gridExtra); library(MASS)
library(clValid); library(clv); library(TraMineRextras); library(simukde)

source("eval_functions.R")
colors_pal  <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                       "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r message=FALSE}
sequences <- read.csv("dat2_s4k5.csv")[,-1]
clust <- read.csv("simulated_Data2nd/sim_seqs_cluster_s4k5.csv")[,-1]
noClust <- read.csv("simulated_Data2nd/sim_seqs_noCluster_s4k5.csv")[,-1]
TVMC_clust <- read.csv("simulated_Data2nd/sim_seqs_cluster_TVMC_s4k5.csv")[,-1]
TVMC_noClust <- read.csv("simulated_Data2nd/sim_seqs_noCluster_TVMC_s4k5.csv")[,-1]
imputed_clust <- read.csv("simulated_Data2nd/sim_seqs_imputed_cluster_s4k5.csv")[,2:1437]
imputed_noClust <- read.csv("simulated_Data2nd/sim_seqs_imputed_noCluster_s4k5.csv")[,2:1437]

sequences_T <- seqdef(sequences)
clust_T <- seqdef(clust)
noClust_T <- seqdef(noClust)
TVMC_clust_T <- seqdef(TVMC_clust)
TVMC_noClust_T <- seqdef(TVMC_noClust)
imputed_clust_T <- seqdef(imputed_clust)
imputed_noClust_T <- seqdef(imputed_noClust)

# sim_list_T <- list(sequences_T, clust_T, noClust_T, TVMC_clust_T, TVMC_noClust_T, imputed_clust_T, imputed_noClust_T)

sim_list_T <- list(sequences_T, TVMC_clust_T, TVMC_noClust_T, imputed_clust_T, imputed_noClust_T)
```



## 1. Plots

```{r}
# for (i in sim_list_T){
#   seqplot(i, border = NA, type = "d", cex.legend = 0.5)
# }
```


## 2. Distribution of state durations (Mean and SD of each activity)

```{r message=FALSE}
this <- lapply(sim_list_T, dist_of_activity_dur)
means <- as.matrix(sapply(this,"[[", 1))
means_prop <- means

for (i in 2:5){
  for (j in 1:4){
    means_prop[j,i] <- paste0(round((means[j,i]/means[j,1] - 1) * 100,1), "%")
  }
}
means <- round(means, 2)
means_prop[,1] <- round(as.vector(as.numeric((means_prop[,1]), 2)), 2)



sds <- as.matrix(sapply(this,"[[", 2))
sds_prop <- sds

for (i in 2:5){
  for (j in 1:4){
    sds_prop[j,i] <- paste0(round((sds[j,i]/sds[j,1] - 1) * 100,1), "%")
  }
}
sds <- round(sds, 2)
sds_prop[,1] <- round(as.vector(as.numeric((sds_prop[,1]), 2)), 2)
```

## 3. Distribution of number of distinct states (Mean and SD)

```{r}
dists <- lapply(sim_list_T, num_of_distinct_states)

means <- sapply(dists, mean)
round(means, 2)
sds <- sapply(dists, sd)
round(sds, 2)
```


## 4. Distribution of entropies (and K-S test statistic p-value against original sequences)

D statistic from K-S test:

original vs clust 0.163

original vs noclust 0.1815

original vs TVMC clust 0.2045

original vs TVMC noclust 0.321

original vs imputed clust 0.159

original vs imputed noclust 0.192


```{r message=FALSE, warning=FALSE}
entropies <- lapply(sim_list_T, TraMineR::seqient)

pvalues <- c()
for (i in 2:5){
  pvalues <- c(pvalues, ks.test(entropies[[1]], entropies[[i]])$p.value)
}

pvalues

dist_dat_entropies <- as.data.frame(cbind(c(entropies[[1]], entropies[[2]], entropies[[3]], entropies[[4]], entropies[[5]]), c(rep("Clustered",2000),rep("Clustered",2000), rep("Not Clustered",2000), rep("Clustered",2000),rep("Not Clustered",2000)), c(rep("Original", 2000),rep("TVMC",2000*2), rep("paired-MC",2000*2))))

colnames(dist_dat_entropies) <- c("Length", "Cluster", "Type")
dist_dat_entropies$Length <- as.numeric(dist_dat_entropies$Length)
dist_dat_entropies$Type <- factor(dist_dat_entropies$Type, levels = c("Original", "TVMC", "paired-MC"))

ggplot(data = dist_dat_entropies, aes(x = Length)) +
  facet_grid(Cluster ~ Type) +
  geom_histogram(binwidth = 0.02) +
  theme_bw() +
  xlab("Distribution of entropy")
```

## 5. Distribution of daily hours spent on states (and K-S test statistic p-value against original sequences)


### 1

```{r message=FALSE, warning=FALSE}
dists_1 <- lapply(sim_list_T, length_of_certain_activity, activity = "1")

pvalues_1 <- c()
for (i in 2:5){
  pvalues_1 <- c(pvalues_1, ks.test(dists_1[[1]], dists_1[[i]])$p.value)
}

pvalues_1

dist_dat_1 <- as.data.frame(cbind(c(dists_1[[1]], dists_1[[2]], dists_1[[3]], dists_1[[4]], dists_1[[5]]), c(rep("Clustered",2000),rep("Clustered",2000), rep("Not Clustered",2000), rep("Clustered",2000),rep("Not Clustered",2000)), c(rep("Original", 2000),rep("TVMC",2000*2), rep("paired-MC",2000*2))))

colnames(dist_dat_1) <- c("Length", "Cluster", "Type")
dist_dat_1$Length <- as.numeric(dist_dat_1$Length)
dist_dat_1$Type <- factor(dist_dat_1$Type, levels = c("Original", "TVMC", "paired-MC"))

ggplot(data = dist_dat_1, aes(x = Length)) +
  facet_grid(Cluster ~ Type) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```

```{r}
dat_1 <- create_ecdf_data(dists_1, 1436)

ggplot(data = dat_1, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") +  # we used GAM on human activity sequences
  labs(x = "State 1 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:5], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered")) +
  xlim(0, 1436) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


### 2


```{r message=FALSE, warning=FALSE}
dists_2 <- lapply(sim_list_T, length_of_certain_activity, activity = "2")

pvalues_2 <- c()
for (i in 2:5){
  pvalues_2 <- c(pvalues_2, ks.test(dists_2[[1]], dists_2[[i]])$p.value)
}

pvalues_2

dist_dat_2 <- as.data.frame(cbind(c(dists_2[[1]], dists_2[[2]], dists_2[[3]], dists_2[[4]], dists_2[[5]]), c(rep("Clustered",2000),rep("Clustered",2000), rep("Not Clustered",2000), rep("Clustered",2000),rep("Not Clustered",2000)), c(rep("Original", 2000),rep("TVMC",2000*2), rep("paired-MC",2000*2))))

colnames(dist_dat_2) <- c("Length", "Cluster", "Type")
dist_dat_2$Length <- as.numeric(dist_dat_2$Length)
dist_dat_2$Type <- factor(dist_dat_2$Type, levels = c("Original","TVMC", "paired-MC"))

ggplot(data = dist_dat_2, aes(x = Length)) +
  facet_grid(Cluster ~ Type) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```

```{r}
dat_2 <- create_ecdf_data(dists_2, 1436)

ggplot(data = dat_2, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "State 2 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:5], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered")) +
  xlim(0, 1436) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


### 3

Due to the sparsity of these activities, all p-values are 0.

D statistic from K-S test:

original vs clust 0.186

original vs noclust 0.2435

original vs TVMC clust 0.195

original vs TVMC noclust 0.353

original vs imputed clust 0.185

original vs imputed noclust 0.253


```{r message=FALSE, warning=FALSE}
dists_3 <- lapply(sim_list_T, length_of_certain_activity, activity = "3")

pvalues_3 <- c()
for (i in 2:5){
  pvalues_3 <- c(pvalues_3, ks.test(dists_3[[1]], dists_3[[i]])$p.value)
}

pvalues_3

dist_dat_3 <- as.data.frame(cbind(c(dists_3[[1]], dists_3[[2]], dists_3[[3]], dists_3[[4]], dists_3[[5]]), c(rep("Clustered",2000),rep("Clustered",2000), rep("Not Clustered",2000), rep("Clustered",2000),rep("Not Clustered",2000)), c(rep("Original", 2000),rep("TVMC",2000*2), rep("paired-MC",2000*2))))


colnames(dist_dat_3) <- c("Length", "Cluster", "Type")
dist_dat_3$Length <- as.numeric(dist_dat_3$Length)
dist_dat_3$Type <- factor(dist_dat_3$Type, levels = c("Original","TVMC", "paired-MC"))

ggplot(data = dist_dat_3, aes(x = Length)) +
  facet_grid(Cluster ~ Type) +
  geom_histogram() +
  theme_bw()
```

```{r}
dat_3 <- create_ecdf_data(dists_3, 1436)

ggplot(data = dat_3, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "State 3 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:5], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered")) +
  xlim(0, 600) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```



### 4

D statistic from K-S test:

original vs clust 0.271

original vs noclust 0.323

original vs TVMC clust 0.2965

original vs TVMC noclust 0.3825

original vs imputed clust 0.2715

original vs imputed noclust 0.3175

```{r message=FALSE, warning=FALSE}
dists_4 <- lapply(sim_list_T, length_of_certain_activity, activity = "4")

pvalues_4 <- c()
for (i in 2:5){
  pvalues_4 <- c(pvalues_4, ks.test(dists_4[[1]], dists_4[[i]])$p.value)
}

pvalues_4

dist_dat_4 <- as.data.frame(cbind(c(dists_4[[1]], dists_4[[2]], dists_4[[3]], dists_4[[4]], dists_4[[5]]), c(rep("Clustered",2000),rep("Clustered",2000), rep("Not Clustered",2000), rep("Clustered",2000),rep("Not Clustered",2000)), c(rep("Original", 2000),rep("TVMC",2000*2), rep("paired-MC",2000*2))))


colnames(dist_dat_4) <- c("Length", "Cluster", "Type")
dist_dat_4$Length <- as.numeric(dist_dat_4$Length)
dist_dat_4$Type <- factor(dist_dat_4$Type, levels = c("Original","TVMC", "paired-MC"))

ggplot(data = dist_dat_4, aes(x = Length)) +
  facet_grid(Cluster ~ Type) +
  geom_histogram() +
  theme_bw()
```

```{r}
dat_4 <- create_ecdf_data(dists_4, 1436)

ggplot(data = dat_4, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "State 4 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:5], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered")) +
  xlim(0, 300) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```



I think the overall message is that for *long* sequential categorical data with few or many categories, there are no tools to simulate sequences without losing resolution. (Felt like there would be more tools for the second data.)



## NEW

### State 1

```{r message=FALSE, warning=FALSE}
dists_1 <- lapply(sim_list_T, dist_of_state, activity = "1")

pvalues_1 <- c()
for (i in 2:5){
  pvalues_1 <- c(pvalues_1, ks.test(dists_1[[1]], dists_1[[i]])$p.value)
}

pvalues_1

dist_dat_1 <- as.data.frame(cbind(c(dists_1[[1]], dists_1[[2]], dists_1[[3]], dists_1[[4]], dists_1[[5]]), c(rep("Clustered",2000),rep("Clustered",2000), rep("Not Clustered",2000), rep("Clustered",2000),rep("Not Clustered",2000)), c(rep("Original", 2000),rep("TVMC",2000*2), rep("paired-MC",2000*2))))

colnames(dist_dat_1) <- c("Length", "Cluster", "Type")
dist_dat_1$Length <- as.numeric(dist_dat_1$Length)
dist_dat_1$Type <- factor(dist_dat_1$Type, levels = c("Original", "TVMC", "paired-MC"))

ggplot(data = dist_dat_1, aes(x = Length)) +
  facet_grid(Cluster ~ Type) +
  geom_histogram(binwidth = 30) +
  theme_bw()


dat_1 <- create_ecdf_data(dists_1, 1436)

ggplot(data = dat_1, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") +  # we used GAM on human activity sequences
  labs(x = "State 1 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:5], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered")) +
  xlim(0, 1436) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


```{r message=FALSE, warning=FALSE}
dists_2 <- lapply(sim_list_T, dist_of_state, activity = "2")

pvalues_2 <- c()
for (i in 2:5){
  pvalues_2 <- c(pvalues_2, ks.test(dists_2[[1]], dists_2[[i]])$p.value)
}

pvalues_2

dist_dat_2 <- as.data.frame(cbind(c(dists_2[[1]], dists_2[[2]], dists_2[[3]], dists_2[[4]], dists_2[[5]]), c(rep("Clustered",2000),rep("Clustered",2000), rep("Not Clustered",2000), rep("Clustered",2000),rep("Not Clustered",2000)), c(rep("Original", 2000),rep("TVMC",2000*2), rep("paired-MC",2000*2))))

colnames(dist_dat_2) <- c("Length", "Cluster", "Type")
dist_dat_2$Length <- as.numeric(dist_dat_2$Length)
dist_dat_2$Type <- factor(dist_dat_2$Type, levels = c("Original","TVMC", "paired-MC"))

ggplot(data = dist_dat_2, aes(x = Length)) +
  facet_grid(Cluster ~ Type) +
  geom_histogram(binwidth = 30) +
  theme_bw()


dat_2 <- create_ecdf_data(dists_2, 1436)

ggplot(data = dat_2, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "State 2 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:5], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered")) +
  xlim(0, 1436) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


### 3


```{r message=FALSE, warning=FALSE}
dists_3 <- lapply(sim_list_T, dist_of_state, activity = "3")

pvalues_3 <- c()
for (i in 2:5){
  pvalues_3 <- c(pvalues_3, ks.test(dists_3[[1]], dists_3[[i]])$p.value)
}

pvalues_3

dist_dat_3 <- as.data.frame(cbind(c(dists_3[[1]], dists_3[[2]], dists_3[[3]], dists_3[[4]], dists_3[[5]]), c(rep("Clustered",2000),rep("Clustered",2000), rep("Not Clustered",2000), rep("Clustered",2000),rep("Not Clustered",2000)), c(rep("Original", 2000),rep("TVMC",2000*2), rep("paired-MC",2000*2))))


colnames(dist_dat_3) <- c("Length", "Cluster", "Type")
dist_dat_3$Length <- as.numeric(dist_dat_3$Length)
dist_dat_3$Type <- factor(dist_dat_3$Type, levels = c("Original","TVMC", "paired-MC"))

ggplot(data = dist_dat_3, aes(x = Length)) +
  facet_grid(Cluster ~ Type) +
  geom_histogram() +
  theme_bw()


dat_3 <- create_ecdf_data(dists_3, 1436)

ggplot(data = dat_3, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "State 3 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:5], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered")) +
  xlim(0, 600) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```



### 4

```{r message=FALSE, warning=FALSE}
dists_4 <- lapply(sim_list_T, dist_of_state, activity = "4")

pvalues_4 <- c()
for (i in 2:5){
  pvalues_4 <- c(pvalues_4, ks.test(dists_4[[1]], dists_4[[i]])$p.value)
}

pvalues_4

dist_dat_4 <- as.data.frame(cbind(c(dists_4[[1]], dists_4[[2]], dists_4[[3]], dists_4[[4]], dists_4[[5]]), c(rep("Clustered",2000),rep("Clustered",2000), rep("Not Clustered",2000), rep("Clustered",2000),rep("Not Clustered",2000)), c(rep("Original", 2000),rep("TVMC",2000*2), rep("paired-MC",2000*2))))


colnames(dist_dat_4) <- c("Length", "Cluster", "Type")
dist_dat_4$Length <- as.numeric(dist_dat_4$Length)
dist_dat_4$Type <- factor(dist_dat_4$Type, levels = c("Original","TVMC", "paired-MC"))

ggplot(data = dist_dat_4, aes(x = Length)) +
  facet_grid(Cluster ~ Type) +
  geom_histogram() +
  theme_bw()

dat_4 <- create_ecdf_data(dists_4, 1436)

ggplot(data = dat_4, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "State 4 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:5], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered")) +
  xlim(0, 120) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


## Dist of states

```{r}
func <- function(state){
  dists <- lapply(sim_list_T, dist_of_state, activity = state)
  means_state <- unlist(lapply(dists, mean))
  sds_state <- unlist(lapply(dists, sd))
  means <- round(means_state, 2)
  sds <- round(sds_state, 2)
  return(rbind(means, sds))
}

all_states <- seqstatl(sequences)

a1 <- func(all_states[1])
a2 <- func(all_states[2])
a3 <- func(all_states[3])
a4 <- func(all_states[4])


table <- data.frame(rbind(a1, a2, a3, a4))
table <- cbind(rep(all_states, each = 2), table)
```


## Count of states


```{r}
counts_1 <- lapply(sim_list_T, count_of_state, activity = "1")
(means_1 <- unlist(lapply(counts_1, mean)))
(sds_1 <- unlist(lapply(counts_1, sd)))


counts_2 <- lapply(sim_list_T, count_of_state, activity = "2")
(means_2 <- unlist(lapply(counts_2, mean)))
(sds_2 <- unlist(lapply(counts_2, sd)))


counts_3 <- lapply(sim_list_T, count_of_state, activity = "3")
(means_3 <- unlist(lapply(counts_3, mean)))
(sds_3 <- unlist(lapply(counts_3, sd)))


counts_4 <- lapply(sim_list_T, count_of_state, activity = "4")
(means_4 <- unlist(lapply(counts_4, mean)))
(sds_4 <- unlist(lapply(counts_4, sd)))
```

## 6. Turbulence

```{r}
turbulence <- lapply(sim_list_T, TraMineR::seqST)

pvalues <- c()
for (i in 2:5){
  pvalues <- c(pvalues, ks.test(turbulence[[1]], turbulence[[i]])$p.value)
}

pvalues
```

## 7. Complexity index

```{r}
complexity <- lapply(sim_list_T, TraMineR::seqici)

pvalues <- c()
for (i in 2:5){
  pvalues <- c(pvalues, ks.test(complexity[[1]], complexity[[i]])$p.value)
}

pvalues
```
