---
title: "Model evaluations"
author: "Zuofu Huang"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse); library(ggplot2); library(lubridate); library(TraMineR); library(performance)
library(GLMMadaptive); library(pscl); library(gridExtra); library(MASS)
library(clValid); library(clv); library(TraMineRextras); library(simukde)

source("../sim_3nd_data/eval_functions.R")
```


```{r}
# "baseline" sequence
sequences <- read.csv("../sim_3nd_data/dat2_s4k5.csv")[,-1]
```

```{r}
# "basic" synthesis on imputed sequences (cluster/no cluster + order 1/2)
imputed_cluster <- read.csv("../sim_3nd_data/simulated_Data2nd/sim_seqs_imputed_cluster_s4k5.csv")[,2:1437]
imputed_noCluster <- read.csv("../sim_3nd_data/simulated_Data2nd/sim_seqs_imputed_noCluster_s4k5.csv")[,2:1437]
```

```{r}
# Investigate effect of time window (30min/60min/120min) on imputed KDE sequences
imputed_cluster_30 <- read.csv("../sim_3nd_data/simulated_Data2nd/different delta/sim_seqs_imputed_cluster_30min_s4k5.csv")[,2:1437]
imputed_noCluster_30 <- read.csv("../sim_3nd_data/simulated_Data2nd/different delta/sim_seqs_imputed_noCluster_30min_s4k5.csv")[,2:1437]

imputed_cluster_30 <- read.csv("../sim_3nd_data/simulated_Data2nd/different delta/sim_seqs_imputed_cluster_30min_s4k5.csv")[,2:1437]
imputed_noCluster_30 <- read.csv("../sim_3nd_data/simulated_Data2nd/different delta/sim_seqs_imputed_noCluster_30min_s4k5.csv")[,2:1437]
```


## Create TramineR objects

```{r message=FALSE, warning=FALSE}
sequences_T <- seqdef(sequences)

imputed_cluster_T <- seqdef(imputed_cluster)
imputed_noCluster_T <- seqdef(imputed_noCluster)

imputed_cluster_30_T <- seqdef(imputed_cluster_30)
imputed_noCluster_30_T <- seqdef(imputed_noCluster_30)

imputed_cluster_30_T <- seqdef(imputed_cluster_30)
imputed_noCluster_30_T <- seqdef(imputed_noCluster_30)
```


```{r}
sim_list_window <- list(sequences, imputed_cluster, imputed_noCluster, imputed_cluster_30, imputed_noCluster_30, imputed_cluster_30, imputed_noCluster_30)

sim_list_window_T <- list(sequences_T, imputed_cluster_T, imputed_noCluster_T, imputed_cluster_30_T, imputed_noCluster_30_T, imputed_cluster_30_T, imputed_noCluster_30_T)
```


# Time window

## 2. Distribution of state durations (Mean and SD of each activity)


```{r}
this <- lapply(sim_list_window_T, dist_of_activity_dur)
means <- as.matrix(sapply(this,"[[", 1))
means_prop <- means

for (i in 2:7){
  for (j in 1:4){
    means_prop[j,i] <- paste0(round((means[j,i]/means[j,1] - 1) * 100,1), "%")
  }
}
means <- round(means, 2)
means_prop[,1] <- round(as.vector(as.numeric((means_prop[,1]), 2)), 2)



sds <- as.matrix(sapply(this,"[[", 2))
sds_prop <- sds

for (i in 2:7){
  for (j in 1:4){
    sds_prop[j,i] <- paste0(round((sds[j,i]/sds[j,1] - 1) * 100,1), "%")
  }
}
sds <- round(sds, 2)
sds_prop[,1] <- round(as.vector(as.numeric((sds_prop[,1]), 2)), 2)
```



## 3. Distribution of number of distinct states (Mean and SD)

```{r}
dists <- lapply(sim_list_window_T, num_of_distinct_states)

means <- sapply(dists, mean)
round(means, 2)
sds <- sapply(dists, sd)
round(sds, 2)
```


## 4. Distribution of entropies (and K-S test statistic p-value against original sequences)

```{r}
entropies <- lapply(sim_list_window_T, TraMineR::seqient)

pvalues <- c()
for (i in 2:7){
  pvalues <- c(pvalues, ks.test(entropies[[1]], entropies[[i]])$p.value)
}

pvalues
```

```{r}
# Consider plots
entropy_dat <- as.data.frame(cbind(c(entropies[[1]], entropies[[2]], entropies[[3]], entropies[[4]], entropies[[5]], entropies[[6]], entropies[[7]]), c(rep("Original data",2000),rep("60 min",2000*2), rep("30 min",2000*2), rep("10 min", 2000*2)), c(rep("Cluster", 2000), rep("Cluster",2000),rep("No cluster",2000),rep("Cluster",2000),rep("No cluster",2000),rep("Cluster",2000),rep("No cluster",2000))))

colnames(entropy_dat) <- c("Length", "Time_window", "Clustered")
entropy_dat$Length <- as.numeric(entropy_dat$Length)
entropy_dat$Time_window <- factor(entropy_dat$Time_window, levels = c("Original data","60 min","30 min", "10 min"))

ggplot(data = entropy_dat, aes(x = Length)) +
  facet_grid(Clustered ~ Time_window) +
  geom_histogram(binwidth = 0.02) +
  theme_bw() + 
  xlab("Distribution of entropy")
```


## 5. Distribution of daily hours spent on work/home states (and K-S test statistic p-value against original sequences)

### 1

```{r}
dists_1 <- lapply(sim_list_window_T, length_of_certain_activity, activity = "1")

pvalues_1 <- c()
for (i in 2:7){
  pvalues_1 <- c(pvalues_1, ks.test(dists_1[[1]], dists_1[[i]])$p.value)
}

pvalues_1

dist_dat_1 <- as.data.frame(cbind(c(dists_1[[1]], dists_1[[2]], dists_1[[3]], dists_1[[4]], dists_1[[5]], dists_1[[6]], dists_1[[7]]), c(rep("Original data",2000),rep("60 min",2000*2), rep("30 min",2000*2), rep("10 min", 2000*2)), c(rep("Cluster", 2000), rep("Cluster",2000),rep("No cluster",2000),rep("Cluster",2000),rep("No cluster",2000),rep("Cluster",2000),rep("No cluster",2000))))

colnames(dist_dat_1) <- c("Length", "Time_window", "Clustered")
dist_dat_1$Length <- as.numeric(dist_dat_1$Length)
dist_dat_1$Time_window <- factor(dist_dat_1$Time_window, levels = c("Original data","60 min","30 min", "10 min"))

ggplot(data = dist_dat_1, aes(x = Length)) +
  facet_grid(Clustered ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```


```{r}
colors_pal  <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                       "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# len: length of the sequence: 1440 for a default daily sequence
create_ecdf_data <- function(distances, len){
  vecs <- c()
  position <- c()
  category <- c()
  ref <- ecdf(distances[[1]])(0:len)
  for (i in 2:length(distances)){
    vecs <- c(vecs, ecdf(distances[[i]])(0:len) - ref)
    position <- c(position, 0:len)
    category <- c(category, rep(i, len+1))
  }
  dat <- as.data.frame(cbind(vecs, position, category))
  dat$category <- as.factor(dat$category)
  return(dat)
}

dat_1 <- create_ecdf_data(dists_1, 1440)

ggplot(data = dat_1, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "State 1 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("60 min clustered", "60 min not clustered", "30 min clustered", "30 min not clustered", "10 min clustered", "10 min not clustered")) +
  xlim(0, 1440) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```



### 2

```{r}
dists_2 <- lapply(sim_list_window_T, length_of_certain_activity, activity = "2")

pvalues_2 <- c()
for (i in 2:7){
  pvalues_2 <- c(pvalues_2, ks.test(dists_2[[1]], dists_2[[i]])$p.value)
}

pvalues_2

dist_dat_2 <- as.data.frame(cbind(c(dists_2[[1]], dists_2[[2]], dists_2[[3]], dists_2[[4]], dists_2[[5]], dists_2[[6]], dists_2[[7]]), c(rep("Original data",2000),rep("60 min",2000*2), rep("30 min",2000*2), rep("10 min", 2000*2)), c(rep("Cluster", 2000), rep("Cluster",2000),rep("No cluster",2000),rep("Cluster",2000),rep("No cluster",2000),rep("Cluster",2000),rep("No cluster",2000))))

colnames(dist_dat_2) <- c("Length", "Time_window", "Clustered")
dist_dat_2$Length <- as.numeric(dist_dat_2$Length)
dist_dat_2$Time_window <- factor(dist_dat_2$Time_window, levels = c("Original data","60 min","30 min", "10 min"))

ggplot(data = dist_dat_2, aes(x = Length)) +
  facet_grid(Clustered ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```

```{r}
dat_2 <- create_ecdf_data(dists_2, 1440)

ggplot(data = dat_2, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "State 2 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("60 min clustered", "60 min not clustered", "30 min clustered", "30 min not clustered", "10 min clustered", "10 min not clustered")) +
  xlim(0, 1440) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```





### 3

```{r}
dists_3 <- lapply(sim_list_window_T, length_of_certain_activity, activity = "3")

pvalues_3 <- c()
for (i in 2:7){
  pvalues_3 <- c(pvalues_3, ks.test(dists_3[[1]], dists_3[[i]])$p.value)
}

pvalues_3

dist_dat_3 <- as.data.frame(cbind(c(dists_3[[1]], dists_3[[2]], dists_3[[3]], dists_3[[4]], dists_3[[5]], dists_3[[6]], dists_3[[7]]), c(rep("Original data",2000),rep("60 min",2000*2), rep("30 min",2000*2), rep("10 min", 2000*2)), c(rep("Cluster", 2000), rep("Cluster",2000),rep("No cluster",2000),rep("Cluster",2000),rep("No cluster",2000),rep("Cluster",2000),rep("No cluster",2000))))

colnames(dist_dat_3) <- c("Length", "Time_window", "Clustered")
dist_dat_3$Length <- as.numeric(dist_dat_3$Length)
dist_dat_3$Time_window <- factor(dist_dat_3$Time_window, levels = c("Original data","60 min","30 min", "10 min"))

ggplot(data = dist_dat_3, aes(x = Length)) +
  facet_grid(Clustered ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```

```{r}
dat_3 <- create_ecdf_data(dists_3, 1440)

ggplot(data = dat_3, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "State 3 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("60 min clustered", "60 min not clustered", "30 min clustered", "30 min not clustered", "10 min clustered", "10 min not clustered")) +
  xlim(0, 1440) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```




### 4

```{r}
dists_4 <- lapply(sim_list_window_T, length_of_certain_activity, activity = "4")

pvalues_4 <- c()
for (i in 2:7){
  pvalues_4 <- c(pvalues_4, ks.test(dists_4[[1]], dists_4[[i]])$p.value)
}

pvalues_4

dist_dat_4 <- as.data.frame(cbind(c(dists_4[[1]], dists_4[[2]], dists_4[[3]], dists_4[[4]], dists_4[[5]], dists_4[[6]], dists_4[[7]]), c(rep("Original data",2000),rep("60 min",2000*2), rep("30 min",2000*2), rep("10 min", 2000*2)), c(rep("Cluster", 2000), rep("Cluster",2000),rep("No cluster",2000),rep("Cluster",2000),rep("No cluster",2000),rep("Cluster",2000),rep("No cluster",2000))))

colnames(dist_dat_4) <- c("Length", "Time_window", "Clustered")
dist_dat_4$Length <- as.numeric(dist_dat_4$Length)
dist_dat_4$Time_window <- factor(dist_dat_4$Time_window, levels = c("Original data","60 min","30 min", "10 min"))

ggplot(data = dist_dat_4, aes(x = Length)) +
  facet_grid(Clustered ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```

```{r}
dat_4 <- create_ecdf_data(dists_4, 1440)

ggplot(data = dat_4, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "State 4 durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("60 min clustered", "60 min not clustered", "30 min clustered", "30 min not clustered", "10 min clustered", "10 min not clustered")) +
  xlim(0, 1440) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


## Others:

Sum of percentage of each state at each time squared

```{r}
sapply(sim_list_window_T, sum_of_state_pct, ref = sequences_T)
```


```{r}
num_distinct_periods_perday(sim_list_window_T[[1]], "WORK")
```

