---
title: "Model evaluations"
author: "Zuofu Huang"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse); library(ggplot2); library(lubridate); library(TraMineR); library(performance)
library(GLMMadaptive); library(pscl); library(gridExtra); library(MASS)
library(clValid); library(clv); library(TraMineRextras); library(simukde)

source("../simseq_Func/eval_functions.R")
```


```{r}
# "baseline" sequence
sequences <- read.csv("../Data in use/original_seqs.csv")[,-1]
```


```{r}
# TVMC on original sequences
# cluster_TVMC <- read.csv("../Data in use/sim_seqs_cluster_TVMC.csv")[,-1]
# noCluster_TVMC <- read.csv("../Data in use/sim_seqs_noCluster_TVMC.csv")[,-1]
```


```{r}
# "basic" synthesis on original sequences (cluster/no cluster + order 1/2)
# cluster <- read.csv("../Data in use/sim_seqs_cluster.csv")[,-1]
# noCluster <- read.csv("../Data in use/sim_seqs_noCluster.csv")[,-1]
# 
# cluster_order2 <- read.csv("../Data in use/sim_seqs_cluster_order2.csv")[,-1]
# noCluster_order2 <- read.csv("../Data in use/sim_seqs_noCluster_order2.csv")[,-1]
```


```{r}
# "basic" synthesis on imputed sequences (cluster/no cluster + order 1/2)
imputed_cluster <- read.csv("../Data in use/sim_seqs_imputed_cluster.csv")[,2:1441]
imputed_noCluster <- read.csv("../Data in use/sim_seqs_imputed_noCluster.csv")[,2:1441]

imputed_cluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_cluster_order2.csv")[,2:1441]
imputed_noCluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_order2.csv")[,2:1441]
```




```{r}
# KDE synthesis on imputed sequences (cluster/no cluster + order 1/2)
# imputed_KDE_cluster <- read.csv("../Data in use/sim_seqs_imputed_KDE_cluster.csv")[,2:1441]
# imputed_KDE_noCluster <- read.csv("../Data in use/sim_seqs_imputed_KDE_noCluster.csv")[,2:1441]
# 
# imputed_KDE_cluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_KDE_cluster_order2.csv")[,2:1441]
# imputed_KDE_noCluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_KDE_noCluster_order2.csv")[,2:1441]
```


```{r}
# logspline
# imputed_log_cluster <- read.csv("../Data in use/sim_seqs_imputed_log_cluster.csv")[,2:1441]
# imputed_log_noCluster <- read.csv("../Data in use/sim_seqs_imputed_log_noCluster.csv")[,2:1441]
# 
# imputed_log_cluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_log_cluster_order2.csv")[,2:1441]
# imputed_log_noCluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_log_noCluster_order2.csv")[,2:1441]
```


```{r}
# Investigate effect of time window (30min/60min/120min) on imputed KDE sequences
imputed_cluster_30 <- read.csv("../Data in use/sim_seqs_imputed_cluster_30min.csv")[,2:1441]
# imputed_noCluster_30 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_30min.csv")[,2:1441]
# 
imputed_cluster_120 <- read.csv("../Data in use/sim_seqs_imputed_cluster_120min.csv")[,2:1441]
# imputed_noCluster_120 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_120min.csv")[,2:1441]
# 
imputed_cluster_order2_30 <- read.csv("../Data in use/sim_seqs_imputed_cluster_order2_30min.csv")[,2:1441]
# imputed_noCluster_order2_30 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_order2_30min.csv")[,2:1441]
# 
imputed_cluster_order2_120 <- read.csv("../Data in use/sim_seqs_imputed_cluster_order2_120min.csv")[,2:1441]
# imputed_noCluster_order2_120 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_order2_120min.csv")[,2:1441]
```


## Create TramineR objects

```{r message=FALSE, warning=FALSE}
# "baseline" sequences
sequences_T <- seqdef(sequences)
```


```{r message=FALSE, warning=FALSE}
# TVMC on original sequences
# cluster_TVMC_T <- seqdef(cluster_TVMC)
# noCluster_TVMC_T <- seqdef(noCluster_TVMC)
```


```{r message=FALSE, warning=FALSE}
# "basic" synthesis on original sequences (cluster/no cluster + order 1/2)
# cluster_T <- seqdef(cluster)
# noCluster_T <- seqdef(noCluster)
# 
# cluster_order2_T <- seqdef(cluster_order2)
# noCluster_order2_T <- seqdef(noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# "basic" synthesis on imputed sequences (cluster/no cluster + order 1/2)
imputed_cluster_T <- seqdef(imputed_cluster)
imputed_noCluster_T <- seqdef(imputed_noCluster)

imputed_cluster_order2_T <- seqdef(imputed_cluster_order2)
imputed_noCluster_order2_T <- seqdef(imputed_noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# KDE synthesis on imputed sequences (cluster/no cluster + order 1/2)
# imputed_KDE_cluster_T <- seqdef(imputed_KDE_cluster)
# imputed_KDE_noCluster_T <- seqdef(imputed_KDE_noCluster)
# 
# imputed_KDE_cluster_order2_T <- seqdef(imputed_KDE_cluster_order2)
# imputed_KDE_noCluster_order2_T <- seqdef(imputed_KDE_noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# logspline on imputed sequences (cluster/no cluster + order 1/2)
# imputed_log_cluster_T <- seqdef(imputed_log_cluster)
# imputed_log_noCluster_T <- seqdef(imputed_log_noCluster)
# 
# imputed_log_cluster_order2_T <- seqdef(imputed_log_cluster_order2)
# imputed_log_noCluster_order2_T <- seqdef(imputed_log_noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# Investigate effect of time window (30min/60min/120min) on imputed sequences
imputed_cluster_30_T <- seqdef(imputed_cluster_30)
# imputed_noCluster_30_T <- seqdef(imputed_noCluster_30)
# 
imputed_cluster_120_T <- seqdef(imputed_cluster_120)
# imputed_noCluster_120_T <- seqdef(imputed_noCluster_120)
# 
imputed_cluster_order2_30_T <- seqdef(imputed_cluster_order2_30)
# imputed_noCluster_order2_30_T <- seqdef(imputed_noCluster_order2_30)
# 
imputed_cluster_order2_120_T <- seqdef(imputed_cluster_order2_120)
# imputed_noCluster_order2_120_T <- seqdef(imputed_noCluster_order2_120)
```


```{r}
sim_list_window <- list(sequences, imputed_cluster, imputed_cluster_order2, imputed_cluster_30, imputed_cluster_order2_30, imputed_cluster_120, imputed_cluster_order2_120)

sim_list_window_T <- list(sequences_T, imputed_cluster_T, imputed_cluster_order2_T, imputed_cluster_30_T, imputed_cluster_order2_30_T, imputed_cluster_120_T, imputed_cluster_order2_120_T)
```


# Time window

## 2. Distribution of state durations (Mean and SD of each activity)


```{r}
this <- lapply(sim_list_window_T, dist_of_activity_dur)
means <- as.matrix(sapply(this,"[[", 1))
means_prop <- means

for (i in 2:7){
  for (j in 1:13){
    means_prop[j,i] <- paste0(round((means[j,i]/means[j,1] - 1) * 100,1), "%")
  }
}
means <- round(means, 2)
means_prop[,1] <- round(as.vector(as.numeric((means_prop[,1]), 2)), 2)



sds <- as.matrix(sapply(this,"[[", 2))
sds_prop <- sds

for (i in 2:7){
  for (j in 1:13){
    sds_prop[j,i] <- paste0(round((sds[j,i]/sds[j,1] - 1) * 100,1), "%")
  }
}
sds <- round(sds, 2)
sds_prop[,1] <- round(as.vector(as.numeric((sds_prop[,1]), 2)), 2)
```



## 3. Distribution of number of distinct states (Mean and SD)

```{r}
dists <- lapply(sim_list_window_T, num_of_distinct_states)

means <- sapply(dists, mean)
round(means, 2)
sds <- sapply(dists, sd)
round(sds, 2)
```


## 4. Distribution of entropies (and K-S test statistic p-value against original sequences)

```{r}
entropies <- lapply(sim_list_window_T, TraMineR::seqient)

pvalues <- c()
for (i in 2:7){
  pvalues <- c(pvalues, ks.test(entropies[[1]], entropies[[i]])$p.value)
}

pvalues
```

```{r}
# Consider plots
entropy_dat <- as.data.frame(cbind(c(entropies[[1]], entropies[[2]], entropies[[3]], entropies[[4]], entropies[[5]], entropies[[6]], entropies[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(entropy_dat) <- c("Length", "Time_window", "Order")
entropy_dat$Length <- as.numeric(entropy_dat$Length)
entropy_dat$Time_window <- factor(entropy_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

ggplot(data = entropy_dat, aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 0.02) +
  theme_bw() + 
  xlab("Distribution of entropy")
```


## 5. Distribution of daily hours spent on work/home states (and K-S test statistic p-value against original sequences)

### **WORK**

```{r}
dists <- lapply(sim_list_window_T, length_of_certain_activity, activity = "WORK")

pvalues_work <- c()
for (i in 2:7){
  pvalues_work <- c(pvalues_work, ks.test(dists[[1]], dists[[i]])$p.value)
}



pvalues_work

work_dist_dat <- as.data.frame(cbind(c(dists[[1]], dists[[2]], dists[[3]], dists[[4]], dists[[5]], dists[[6]], dists[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(work_dist_dat) <- c("Length", "Time_window", "Order")
work_dist_dat$Length <- as.numeric(work_dist_dat$Length)
work_dist_dat$Time_window <- factor(work_dist_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

ggplot(data = work_dist_dat, aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()

ggplot(data = work_dist_dat[work_dist_dat$Length != 0,], aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```


```{r}
colors_pal  <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                       "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# len: length of the sequence: 1440 for a default daily sequence
create_ecdf_data <- function(distances, len){
  vecs <- c()
  position <- c()
  category <- c()
  ref <- ecdf(distances[[1]])(0:len)
  for (i in 2:length(distances)){
    vecs <- c(vecs, ecdf(distances[[i]])(0:len) - ref)
    position <- c(position, 0:len)
    category <- c(category, rep(i, len+1))
  }
  dat <- as.data.frame(cbind(vecs, position, category))
  dat$category <- as.factor(dat$category)
  return(dat)
}

dat <- create_ecdf_data(dists, 1440)

ggplot(data = dat, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Work durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("60 min order 1", "60 min order 2", "30 min order 1", "30 min order 2", "120 min order 1", "120 min order 2")) +
  xlim(0, 1440) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")

dists_no0 <- lapply(dists, function(x) x[which(x!=0)])
dat_no0 <- create_ecdf_data(dists_no0, 1440)

ggplot(data = dat_no0, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Work durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("60 min order 1", "60 min order 2", "30 min order 1", "30 min order 2", "120 min order 1", "120 min order 2")) +
  xlim(0, 1440) + 
  ylim(-0.3,0.3) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```



### **HOME**

```{r}
dists_home <- lapply(sim_list_window_T, length_of_certain_activity, activity = "HOME")

pvalues_home <- c()
for (i in 2:7){
  pvalues_home <- c(pvalues_home, ks.test(dists_home[[1]], dists_home[[i]])$p.value)
}

pvalues_home

home_dist_dat <- as.data.frame(cbind(c(dists_home[[1]], dists_home[[2]], dists_home[[3]], dists_home[[4]], dists_home[[5]], dists_home[[6]], dists_home[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(home_dist_dat) <- c("Length", "Time_window", "Order")
home_dist_dat$Length <- as.numeric(home_dist_dat$Length)
home_dist_dat$Time_window <- factor(home_dist_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

ggplot(data = home_dist_dat, aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()

ggplot(data = home_dist_dat[home_dist_dat$Length != 1440,], aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```

```{r}
dat_home <- create_ecdf_data(dists_home, 1440)

ggplot(data = dat_home, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Home durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("60 min order 1", "60 min order 2", "30 min order 1", "30 min order 2", "120 min order 1", "120 min order 2")) +
  xlim(0, 1440) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")

dists_home_no1440 <- lapply(dists_home, function(x) x[which(x!=1440)])
dat_home_no1440 <- create_ecdf_data(dists_home_no1440, 1440)

ggplot(data = dat_home_no1440, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Home durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("60 min order 1", "60 min order 2", "30 min order 1", "30 min order 2", "120 min order 1", "120 min order 2")) +
  xlim(0, 1440) + 
  ylim(-0.3,0.3) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```





### **CAR**

```{r}
dists_car <- lapply(sim_list_window_T, length_of_certain_activity, activity = "CAR")

pvalues_car <- c()
for (i in 2:7){
  pvalues_car <- c(pvalues_car, ks.test(dists_car[[1]], dists_car[[i]])$p.value)
}

pvalues_car

car_dist_dat <- as.data.frame(cbind(c(dists_car[[1]], dists_car[[2]], dists_car[[3]], dists_car[[4]], dists_car[[5]], dists_car[[6]], dists_car[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(car_dist_dat) <- c("Length", "Time_window", "Order")
car_dist_dat$Length <- as.numeric(car_dist_dat$Length)
car_dist_dat$Time_window <- factor(car_dist_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

ggplot(data = car_dist_dat, aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 5) +
  theme_bw()

# ggplot(data = car_dist_dat[car_dist_dat$Length < 300,], aes(x = Length)) +
#   facet_grid(Order ~ Time_window) +
#   geom_histogram(binwidth = 5) +
#   theme_bw()
```

```{r}
dat_car <- create_ecdf_data(dists_car, 1440)

ggplot(data = dat_car, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Car durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("60 min order 1", "60 min order 2", "30 min order 1", "30 min order 2", "120 min order 1", "120 min order 2")) +
  xlim(0, 240) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")


# dists_car_no0 <- lapply(dists_car, function(x) x[which(x!=0)])
# dat_car_no0 <- create_ecdf_data(dists_car_no0, 1440)
# 
# ggplot(data = dat_car_no0, aes(y = vecs, x = position, group = category, color = category)) +
#   geom_smooth(se = F, method = "gam") + 
#   labs(x = "Car durations", y = "Difference in ecdf") +
#   scale_colour_manual(values = colors_pal[2:7], labels = c("60 min order 1", "60 min order 2", "30 min order 1", "30 min order 2", "120 min order 1", "120 min order 2")) +
#   xlim(0, 240) + # changed from 1440 to 120?
#   ylim(-0.3,0.3) +
#   geom_abline(slope = 0, intercept = 0) + 
#   theme_bw() + 
#   theme(legend.position = "bottom")
```




### **LEISURE_RECREATION**

```{r}
dists_LR <- lapply(sim_list_window_T, length_of_certain_activity, activity = "LEISURE_RECREATION")

pvalues_LR <- c()
for (i in 2:7){
  pvalues_LR <- c(pvalues_LR, ks.test(dists_LR[[1]], dists_LR[[i]])$p.value)
}

pvalues_LR

LR_dist_dat <- as.data.frame(cbind(c(dists_LR[[1]], dists_LR[[2]], dists_LR[[3]], dists_LR[[4]], dists_LR[[5]], dists_LR[[6]], dists_LR[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(LR_dist_dat) <- c("Length", "Time_window", "Order")
LR_dist_dat$Length <- as.numeric(LR_dist_dat$Length)
LR_dist_dat$Time_window <- factor(LR_dist_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

# ggplot(data = LR_dist_dat, aes(x = Length)) +
#   facet_grid(Order ~ Time_window) +
#   geom_histogram(binwidth = 20) +
#   theme_bw()

ggplot(data = LR_dist_dat[LR_dist_dat$Length != 0,], aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 20) +
  theme_bw()
```

```{r}
dists_LR_no0 <- lapply(dists_LR, function(x) x[which(x!=0)])
dat_LR_no0 <- create_ecdf_data(dists_LR_no0, 1440)

ggplot(data = dat_LR_no0, aes(y = vecs, x = position, group = category, color = category)) +
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Leisure/Recreation durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("60 min order 1", "60 min order 2", "30 min order 1", "30 min order 2", "120 min order 1", "120 min order 2")) +
  xlim(0, 1440) +
  ylim(-0.3,0.3) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


### **PERSONAL_BUSINESS**

```{r}
dists_PB <- lapply(sim_list_window_T, length_of_certain_activity, activity = "PERSONAL_BUSINESS")

pvalues_PB <- c()
for (i in 2:7){
  pvalues_PB <- c(pvalues_PB, ks.test(dists_PB[[1]], dists_PB[[i]])$p.value)
}

pvalues_PB

PB_dist_dat <- as.data.frame(cbind(c(dists_PB[[1]], dists_PB[[2]], dists_PB[[3]], dists_PB[[4]], dists_PB[[5]], dists_PB[[6]], dists_PB[[7]]), c(rep("Original data",1929),rep("60 min",1929*2), rep("30 min",1929*2), rep("120 min", 1929*2)), c(rep("Order 1", 1929), rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929),rep("Order 1",1929),rep("Order 2",1929))))

colnames(PB_dist_dat) <- c("Length", "Time_window", "Order")
PB_dist_dat$Length <- as.numeric(PB_dist_dat$Length)
PB_dist_dat$Time_window <- factor(PB_dist_dat$Time_window, levels = c("Original data","60 min","30 min", "120 min"))

# ggplot(data = PB_dist_dat, aes(x = Length)) +
#   facet_grid(Order ~ Time_window) +
#   geom_histogram(binwidth = 30) +
#   theme_bw()

ggplot(data = PB_dist_dat[PB_dist_dat$Length != 0,], aes(x = Length)) +
  facet_grid(Order ~ Time_window) +
  geom_histogram(binwidth = 20) +
  theme_bw()
```

```{r}
dists_PB_no0 <- lapply(dists_PB, function(x) x[which(x!=0)])
dat_PB_no0 <- create_ecdf_data(dists_PB_no0, 1440)

ggplot(data = dat_PB_no0, aes(y = vecs, x = position, group = category, color = category)) +
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Personal business durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("60 min order 1", "60 min order 2", "30 min order 1", "30 min order 2", "120 min order 1", "120 min order 2")) +
  xlim(0, 1440) +
  ylim(-0.3,0.3) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```




## Others:

Sum of percentage of each state at each time squared

```{r}
sapply(sim_list_window_T, sum_of_state_pct, ref = sequences_T)
```


```{r}
num_distinct_periods_perday(sim_list_window_T[[1]], "WORK")
```

