---
title: "Model evaluations"
author: "Zuofu Huang"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse); library(ggplot2); library(lubridate); library(TraMineR); library(performance)
library(GLMMadaptive); library(pscl); library(gridExtra); library(MASS)
library(clValid); library(clv); library(TraMineRextras); library(simukde)

source("eval_functions.R")
```


```{r}
# "baseline" sequence
sequences <- read.csv("../Data in use/original_seqs.csv")[,-1]
```


```{r}
# TVMC on original sequences
cluster_TVMC <- read.csv("../Data in use/sim_seqs_cluster_TVMC.csv")[,-1]
noCluster_TVMC <- read.csv("../Data in use/sim_seqs_noCluster_TVMC.csv")[,-1]
```


```{r}
# "basic" synthesis on original sequences (cluster/no cluster + order 1/2)
cluster <- read.csv("../Data in use/sim_seqs_cluster.csv")[,-1]
noCluster <- read.csv("../Data in use/sim_seqs_noCluster.csv")[,-1]

cluster_order2 <- read.csv("../Data in use/sim_seqs_cluster_order2.csv")[,-1]
noCluster_order2 <- read.csv("../Data in use/sim_seqs_noCluster_order2.csv")[,-1]
```


```{r}
# "basic" synthesis on imputed sequences (cluster/no cluster + order 1/2)
imputed_cluster <- read.csv("../Data in use/sim_seqs_imputed_cluster.csv")[,2:1441]
imputed_noCluster <- read.csv("../Data in use/sim_seqs_imputed_noCluster.csv")[,2:1441]

imputed_cluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_cluster_order2.csv")[,2:1441]
imputed_noCluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_order2.csv")[,2:1441]
```




```{r}
# KDE synthesis on imputed sequences (cluster/no cluster + order 1/2)
imputed_KDE_cluster <- read.csv("../Data in use/sim_seqs_imputed_KDE_cluster.csv")[,2:1441]
imputed_KDE_noCluster <- read.csv("../Data in use/sim_seqs_imputed_KDE_noCluster.csv")[,2:1441]

imputed_KDE_cluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_KDE_cluster_order2.csv")[,2:1441]
imputed_KDE_noCluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_KDE_noCluster_order2.csv")[,2:1441]
```


```{r}
# logspline
imputed_log_cluster <- read.csv("../Data in use/sim_seqs_imputed_log_cluster.csv")[,2:1441]
imputed_log_noCluster <- read.csv("../Data in use/sim_seqs_imputed_log_noCluster.csv")[,2:1441]

imputed_log_cluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_log_cluster_order2.csv")[,2:1441]
imputed_log_noCluster_order2 <- read.csv("../Data in use/sim_seqs_imputed_log_noCluster_order2.csv")[,2:1441]
```


```{r}
# Investigate effect of time window (30min/60min/120min) on imputed KDE sequences
imputed_cluster_30 <- read.csv("../Data in use/sim_seqs_imputed_cluster_30min.csv")[,2:1441]
# imputed_noCluster_30 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_30min.csv")[,2:1441]
# 
imputed_cluster_120 <- read.csv("../Data in use/sim_seqs_imputed_cluster_120min.csv")[,2:1441]
# imputed_noCluster_120 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_120min.csv")[,2:1441]
# 
imputed_cluster_order2_30 <- read.csv("../Data in use/sim_seqs_imputed_cluster_order2_30min.csv")[,2:1441]
# imputed_noCluster_order2_30 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_order2_30min.csv")[,2:1441]
# 
imputed_cluster_order2_120 <- read.csv("../Data in use/sim_seqs_imputed_cluster_order2_120min.csv")[,2:1441]
# imputed_noCluster_order2_120 <- read.csv("../Data in use/sim_seqs_imputed_noCluster_order2_120min.csv")[,2:1441]
```


## Create TramineR objects

```{r message=FALSE, warning=FALSE}
# "baseline" sequences
sequences_T <- seqdef(sequences)

palette <- c("#009292","#FF6DB6","#B6DBFF","#FFB6DB","#490092","#999999","#DB6D00","#004949","#B66DFF","#6DB6FF","#920000","#924900","#006DDB")

seqiplot(seqdef(sequences, cpal = palette), border = NA, cex.legend = 0.5, tlim = sample(1:1929, 100), ylab = NA, xtlab = NA)
```


```{r message=FALSE, warning=FALSE}
# TVMC on original sequences
cluster_TVMC_T <- seqdef(cluster_TVMC)
noCluster_TVMC_T <- seqdef(noCluster_TVMC)
```


```{r message=FALSE, warning=FALSE}
# "basic" synthesis on original sequences (cluster/no cluster + order 1/2)
cluster_T <- seqdef(cluster)
noCluster_T <- seqdef(noCluster)

cluster_order2_T <- seqdef(cluster_order2)
noCluster_order2_T <- seqdef(noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# "basic" synthesis on imputed sequences (cluster/no cluster + order 1/2)
imputed_cluster_T <- seqdef(imputed_cluster)
imputed_noCluster_T <- seqdef(imputed_noCluster)

imputed_cluster_order2_T <- seqdef(imputed_cluster_order2)
imputed_noCluster_order2_T <- seqdef(imputed_noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# KDE synthesis on imputed sequences (cluster/no cluster + order 1/2)
imputed_KDE_cluster_T <- seqdef(imputed_KDE_cluster)
imputed_KDE_noCluster_T <- seqdef(imputed_KDE_noCluster)

imputed_KDE_cluster_order2_T <- seqdef(imputed_KDE_cluster_order2)
imputed_KDE_noCluster_order2_T <- seqdef(imputed_KDE_noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# logspline on imputed sequences (cluster/no cluster + order 1/2)
imputed_log_cluster_T <- seqdef(imputed_log_cluster)
imputed_log_noCluster_T <- seqdef(imputed_log_noCluster)

imputed_log_cluster_order2_T <- seqdef(imputed_log_cluster_order2)
imputed_log_noCluster_order2_T <- seqdef(imputed_log_noCluster_order2)
```


```{r message=FALSE, warning=FALSE}
# Investigate effect of time window (30min/60min/120min) on imputed sequences
imputed_cluster_30_T <- seqdef(imputed_cluster_30)
# imputed_noCluster_30_T <- seqdef(imputed_noCluster_30)
# 
imputed_cluster_120_T <- seqdef(imputed_cluster_120)
# imputed_noCluster_120_T <- seqdef(imputed_noCluster_120)
# 
imputed_cluster_order2_30_T <- seqdef(imputed_cluster_order2_30)
# imputed_noCluster_order2_30_T <- seqdef(imputed_noCluster_order2_30)
# 
imputed_cluster_order2_120_T <- seqdef(imputed_cluster_order2_120)
# imputed_noCluster_order2_120_T <- seqdef(imputed_noCluster_order2_120)
```



```{r}
sim_list <- list(sequences, cluster_TVMC, noCluster_TVMC, imputed_cluster, imputed_noCluster, imputed_cluster_order2, imputed_noCluster_order2)

sim_list_T <- list(sequences_T, cluster_TVMC_T, noCluster_TVMC_T, imputed_cluster_T, imputed_noCluster_T, imputed_cluster_order2_T, imputed_noCluster_order2_T)
```

```{r}
# sim_list_window <- list(sequences, imputed_cluster, imputed_cluster_order2, imputed_cluster_30, imputed_cluster_order2_30, imputed_cluster_120, imputed_cluster_order2_120)
# 
# sim_list_window_T <- list(sequences_T, imputed_cluster_T, imputed_cluster_order2_T, imputed_cluster_30_T, imputed_cluster_order2_30_T, imputed_cluster_120_T, imputed_cluster_order2_120_T)
```



# Main comparisons

Evaluation criteria:

1. Transition matrix and heatmap? (TO BE DEVELOPED)

2. Distribution of state durations (Mean and SD of each activity)

3. Distribution of number of distinct states (Mean and SD)

4. Distribution of entropies (and K-S test statistic p-value against original sequences)

5. Distribution of daily hours spent on work/home states (and K-S test statistic p-value against original sequences)

6. Turbulence


## 2. Distribution of state durations (Mean and SD of each activity)

```{r}
this <- lapply(sim_list_T, dist_of_activity_dur)
means <- as.matrix(sapply(this,"[[", 1))
means_prop <- means

for (i in 2:7){
  for (j in 1:13){
    means_prop[j,i] <- paste0(round((means[j,i]/means[j,1] - 1) * 100,1), "%")
  }
}
means <- round(means, 2)
means_prop[,1] <- round(as.vector(as.numeric((means_prop[,1]), 2)), 2)



sds <- as.matrix(sapply(this,"[[", 2))
sds_prop <- sds

for (i in 2:7){
  for (j in 1:13){
    sds_prop[j,i] <- paste0(round((sds[j,i]/sds[j,1] - 1) * 100,1), "%")
  }
}
sds <- round(sds, 2)
sds_prop[,1] <- round(as.vector(as.numeric((sds_prop[,1]), 2)), 2)
```


### NEW:

```{r}
# new <- sapply(sim_list_T, dist_of_occurrences)
# numbers <- as.data.frame(new[40:78,])
# numbers <- as.data.frame(sapply(numbers, as.numeric))
# numbers <- numbers %>%
#   mutate(across(where(is.numeric), round, digits = 2))
# 
# result <- cbind(as.vector(new[1:39,1]), rep(c("Average occurrence time", "Duration mean", "Duration SD"), 13), numbers)
# 
# colnames(result) <- c("State", "Statistic", "Original\nsequences", "TVMC\ncluster", "TVMC\nno cluster", "paired-MC\ncluster", "paired-MC\nno cluster", "paired-MC order 2\n cluster", "paired-MC order 2\n no cluster")
# 
# write.csv(result, "summarystat.csv")
```



## 3. Distribution of number of distinct states (Mean and SD)

```{r}
dists <- lapply(sim_list_T, num_of_distinct_states)

means <- sapply(dists, mean)
round(means, 2)
sds <- sapply(dists, sd)
round(sds, 2)
```


## 4. Distribution of entropies (and K-S test statistic p-value against original sequences)

```{r}
entropies <- lapply(sim_list_T, TraMineR::seqient)

pvalues <- c()
for (i in 2:7){
  pvalues <- c(pvalues, ks.test(entropies[[1]], entropies[[i]])$p.value)
}

pvalues
```

```{r}
# Consider plots
entropy_dat <- as.data.frame(cbind(c(entropies[[1]], entropies[[2]], entropies[[3]], entropies[[4]], entropies[[5]], entropies[[6]], entropies[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))

colnames(entropy_dat) <- c("Length", "Method", "Clustered")
entropy_dat$Length <- as.numeric(entropy_dat$Length)
entropy_dat$Method <- factor(entropy_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2"))

ggplot(data = entropy_dat, aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 0.02) +
  theme_bw()
```


## 5. Distribution of daily hours spent on work/home states (and K-S test statistic p-value against original sequences)

### **WORK**

```{r}
dists <- lapply(sim_list_T, length_of_certain_activity, activity = "WORK")

pvalues_work <- c()
for (i in 2:7){
  pvalues_work <- c(pvalues_work, ks.test(dists[[1]], dists[[i]])$p.value)
}

pvalues_work

work_dist_dat <- as.data.frame(cbind(c(dists[[1]], dists[[2]], dists[[3]], dists[[4]], dists[[5]], dists[[6]], dists[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))

colnames(work_dist_dat) <- c("Length", "Method", "Clustered")
work_dist_dat$Length <- as.numeric(work_dist_dat$Length)
work_dist_dat$Method <- factor(work_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2"))

ggplot(data = work_dist_dat, aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 30) +
  theme_bw()

ggplot(data = work_dist_dat[work_dist_dat$Length != 0,], aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```


```{r}
colors_pal  <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                       "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# len: length of the sequence: 1440 for a default daily sequence
create_ecdf_data <- function(distances, len){
  vecs <- c()
  position <- c()
  category <- c()
  ref <- ecdf(distances[[1]])(0:len)
  for (i in 2:length(distances)){
    vecs <- c(vecs, ecdf(distances[[i]])(0:len) - ref)
    position <- c(position, 0:len)
    category <- c(category, rep(i, len+1))
  }
  dat <- as.data.frame(cbind(vecs, position, category))
  dat$category <- as.factor(dat$category)
  return(dat)
}

dat <- create_ecdf_data(dists, 1440)

ggplot(data = dat, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Time", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 1440) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")

dists_no0 <- lapply(dists, function(x) x[which(x!=0)])
dat_no0 <- create_ecdf_data(dists_no0, 1440)

ggplot(data = dat_no0, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Time", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 1440) + 
  ylim(-0.3,0.3) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```




### **HOME**

```{r}
dists_home <- lapply(sim_list_T, length_of_certain_activity, activity = "HOME")

pvalues_home <- c()
for (i in 2:7){
  pvalues_home <- c(pvalues_home, ks.test(dists_home[[1]], dists_home[[i]])$p.value)
}

pvalues_home

home_dist_dat <- as.data.frame(cbind(c(dists_home[[1]], dists_home[[2]], dists_home[[3]], dists_home[[4]], dists_home[[5]], dists_home[[6]], dists_home[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))

colnames(home_dist_dat) <- c("Length", "Method", "Clustered")
home_dist_dat$Length <- as.numeric(home_dist_dat$Length)
home_dist_dat$Method <- factor(home_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2"))

ggplot(data = home_dist_dat, aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 30) +
  theme_bw()

ggplot(data = home_dist_dat[home_dist_dat$Length != 1440,], aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 30) +
  theme_bw()
```


```{r}
dat_home <- create_ecdf_data(dists_home, 1440)

ggplot(data = dat_home, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Time", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 1440) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")

dists_home_no1440 <- lapply(dists_home, function(x) x[which(x!=1440)])
dat_home_no1440 <- create_ecdf_data(dists_home_no1440, 1440)

ggplot(data = dat_home_no1440, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Time", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 1440) + 
  ylim(-0.3,0.3) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```




### **car**

```{r}
dists_car <- lapply(sim_list_T, length_of_certain_activity, activity = "CAR")

pvalues_car <- c()
for (i in 2:7){
  pvalues_car <- c(pvalues_car, ks.test(dists_car[[1]], dists_car[[i]])$p.value)
}

pvalues_car

car_dist_dat <- as.data.frame(cbind(c(dists_car[[1]], dists_car[[2]], dists_car[[3]], dists_car[[4]], dists_car[[5]], dists_car[[6]], dists_car[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))

colnames(car_dist_dat) <- c("Length", "Method", "Clustered")
car_dist_dat$Length <- as.numeric(car_dist_dat$Length)
car_dist_dat$Method <- factor(car_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2"))

ggplot(data = car_dist_dat, aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 5) +
  theme_bw()
```


```{r}
dat_car <- create_ecdf_data(dists_car, 1440)

ggplot(data = dat_car, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Time", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 120) +  # changed from 1440 to 120?
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")



dists_car_no0 <- lapply(dists_car, function(x) x[which(x!=0)])
dat_car_no0 <- create_ecdf_data(dists_car_no0, 1440)

ggplot(data = dat_car_no0, aes(y = vecs, x = position, group = category, color = category)) +
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Time", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 120) + # changed from 1440 to 120?
  ylim(-0.3,0.3) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


### **Leisure and recreation**

```{r}
dists_LR <- lapply(sim_list_T, length_of_certain_activity, activity = "LEISURE_RECREATION")

pvalues_LR <- c()
for (i in 2:7){
  pvalues_LR <- c(pvalues_LR, ks.test(dists_LR[[1]], dists_LR[[i]])$p.value)
}

pvalues_LR

LR_dist_dat <- as.data.frame(cbind(c(dists_LR[[1]], dists_LR[[2]], dists_LR[[3]], dists_LR[[4]], dists_LR[[5]], dists_LR[[6]], dists_LR[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))

colnames(LR_dist_dat) <- c("Length", "Method", "Clustered")
LR_dist_dat$Length <- as.numeric(LR_dist_dat$Length)
LR_dist_dat$Method <- factor(LR_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2"))

# ggplot(data = LR_dist_dat, aes(x = Length)) +
#   facet_grid(Clustered ~ Method) +
#   geom_histogram(binwidth = 30) +
#   theme_bw()

ggplot(data = LR_dist_dat[LR_dist_dat$Length != 0,], aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 20) +
  theme_bw()
```


```{r}
dists_LR_no0 <- lapply(dists_LR, function(x) x[which(x!=0)])
dat_LR_no0 <- create_ecdf_data(dists_LR_no0, 1440)

ggplot(data = dat_LR_no0, aes(y = vecs, x = position, group = category, color = category)) +
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Time", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 1440) +
  ylim(-0.3,0.3) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```



### **Personal Business**


```{r}
dists_PB <- lapply(sim_list_T, length_of_certain_activity, activity = "PERSONAL_BUSINESS")

pvalues_PB <- c()
for (i in 2:7){
  pvalues_PB <- c(pvalues_PB, ks.test(dists_PB[[1]], dists_PB[[i]])$p.value)
}

pvalues_PB

PB_dist_dat <- as.data.frame(cbind(c(dists_PB[[1]], dists_PB[[2]], dists_PB[[3]], dists_PB[[4]], dists_PB[[5]], dists_PB[[6]], dists_PB[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))

colnames(PB_dist_dat) <- c("Length", "Method", "Clustered")
PB_dist_dat$Length <- as.numeric(PB_dist_dat$Length)
PB_dist_dat$Method <- factor(PB_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2"))

ggplot(data = PB_dist_dat[PB_dist_dat$Length != 0,], aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 20) +
  theme_bw()
```

```{r}
dists_PB_no0 <- lapply(dists_PB, function(x) x[which(x!=0)])
dat_PB_no0 <- create_ecdf_data(dists_PB_no0, 1440)

ggplot(data = dat_PB_no0, aes(y = vecs, x = position, group = category, color = category)) +
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Time", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 1440) +
  ylim(-0.3,0.3) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


## 4. Distribution of entropies (and K-S test statistic p-value against original sequences)

```{r}
entropies <- lapply(sim_list_T, TraMineR::seqient)

pvalues <- c()
for (i in 2:7){
  pvalues <- c(pvalues, ks.test(entropies[[1]], entropies[[i]])$p.value)
}

pvalues
```

## NEW:

### **WORK**

```{r}
dists <- lapply(sim_list_T, dist_of_state, activity = "WORK")

pvalues_work <- c()
for (i in 2:7){
  pvalues_work <- c(pvalues_work, ks.test(dists[[1]], dists[[i]])$p.value)
}

pvalues_work

work_dist_dat <- as.data.frame(cbind(c(dists[[1]], dists[[2]], dists[[3]], dists[[4]], dists[[5]], dists[[6]], dists[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))

colnames(work_dist_dat) <- c("Length", "Method", "Clustered")
work_dist_dat$Length <- as.numeric(work_dist_dat$Length)
work_dist_dat$Method <- factor(work_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2"))

ggplot(data = work_dist_dat, aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 30) +
  theme_bw()


colors_pal  <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                       "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

dat <- create_ecdf_data(dists, 1440)

ggplot(data = dat, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Work durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 1440) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```




### **HOME**

```{r}
dists_home <- lapply(sim_list_T, dist_of_state, activity = "HOME")

pvalues_home <- c()
for (i in 2:7){
  pvalues_home <- c(pvalues_home, ks.test(dists_home[[1]], dists_home[[i]])$p.value)
}

pvalues_home

home_dist_dat <- as.data.frame(cbind(c(dists_home[[1]], dists_home[[2]], dists_home[[3]], dists_home[[4]], dists_home[[5]], dists_home[[6]], dists_home[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))

colnames(home_dist_dat) <- c("Length", "Method", "Clustered")
home_dist_dat$Length <- as.numeric(home_dist_dat$Length)
home_dist_dat$Method <- factor(home_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2"))

ggplot(data = home_dist_dat, aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 30) +
  theme_bw()


dat_home <- create_ecdf_data(dists_home, 1440)

ggplot(data = dat_home, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Home durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 1440) + 
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```



### **car**

```{r}
dists_car <- lapply(sim_list_T, dist_of_state, activity = "CAR")

pvalues_car <- c()
for (i in 2:7){
  pvalues_car <- c(pvalues_car, ks.test(dists_car[[1]], dists_car[[i]])$p.value)
}

pvalues_car

car_dist_dat <- as.data.frame(cbind(c(dists_car[[1]], dists_car[[2]], dists_car[[3]], dists_car[[4]], dists_car[[5]], dists_car[[6]], dists_car[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))

colnames(car_dist_dat) <- c("Length", "Method", "Clustered")
car_dist_dat$Length <- as.numeric(car_dist_dat$Length)
car_dist_dat$Method <- factor(car_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2"))

ggplot(data = car_dist_dat, aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 5) +
  theme_bw()


dat_car <- create_ecdf_data(dists_car, 1440)

ggplot(data = dat_car, aes(y = vecs, x = position, group = category, color = category)) + 
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Car durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 120) +  # changed from 1440 to 120?
  ylim(-0.15,0.15) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


### **Leisure and recreation**

```{r}
dists_LR <- lapply(sim_list_T, dist_of_state, activity = "LEISURE_RECREATION")

pvalues_LR <- c()
for (i in 2:7){
  pvalues_LR <- c(pvalues_LR, ks.test(dists_LR[[1]], dists_LR[[i]])$p.value)
}

pvalues_LR

LR_dist_dat <- as.data.frame(cbind(c(dists_LR[[1]], dists_LR[[2]], dists_LR[[3]], dists_LR[[4]], dists_LR[[5]], dists_LR[[6]], dists_LR[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))

colnames(LR_dist_dat) <- c("Length", "Method", "Clustered")
LR_dist_dat$Length <- as.numeric(LR_dist_dat$Length)
LR_dist_dat$Method <- factor(LR_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2"))


ggplot(data = LR_dist_dat, aes(x = Length)) +
  facet_grid(Clustered ~ Method) +
  geom_histogram(binwidth = 20) +
  theme_bw()



dat_LR <- create_ecdf_data(dists_LR, 1440)

ggplot(data = dat_LR, aes(y = vecs, x = position, group = category, color = category)) +
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Leisure and recreation durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 1440) +
  ylim(-0.3,0.3) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```



### **Personal Business**


```{r}
dists_PB <- lapply(sim_list_T, dist_of_state, activity = "PERSONAL_BUSINESS")

pvalues_PB <- c()
for (i in 2:7){
  pvalues_PB <- c(pvalues_PB, ks.test(dists_PB[[1]], dists_PB[[i]])$p.value)
}

pvalues_PB

PB_dist_dat <- as.data.frame(cbind(c(dists_PB[[1]], dists_PB[[2]], dists_PB[[3]], dists_PB[[4]], dists_PB[[5]], dists_PB[[6]], dists_PB[[7]]), c(rep("Original data",1929),rep("TVMC",1929*2), rep("Paired-MC order 1",1929*2), rep("Paired-MC order 2", 1929*2)), c(rep("Clustered", 1929), rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929),rep("Clustered",1929),rep("Not Clustered",1929))))

colnames(PB_dist_dat) <- c("Length", "Method", "Clustered")
PB_dist_dat$Length <- as.numeric(PB_dist_dat$Length)
PB_dist_dat$Method <- factor(PB_dist_dat$Method, levels = c("Original data","TVMC","Paired-MC order 1", "Paired-MC order 2"))


dat_PB <- create_ecdf_data(dists_PB, 1440)

ggplot(data = dat_PB, aes(y = vecs, x = position, group = category, color = category)) +
  geom_smooth(se = F, method = "gam") + 
  labs(x = "Personal business durations", y = "Difference in ecdf") +
  scale_colour_manual(values = colors_pal[2:7], labels = c("TVMC clustered", "TVMC not clustered", "paired-MC clustered", "paired-MC not clustered", "paired-MC order 2 clustered", "paired-MC order 2 not clustered")) +
  xlim(0, 1440) +
  ylim(-0.3,0.3) +
  geom_abline(slope = 0, intercept = 0) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```


### Others

```{r}
dists_bike <- lapply(sim_list_T, dist_of_state, activity = "BIKE")

pvalues_bike <- c()
for (i in 2:7){
  pvalues_bike <- c(pvalues_bike, ks.test(dists_bike[[1]], dists_bike[[i]])$p.value)
}

pvalues_bike
```


```{r}
dists_bus <- lapply(sim_list_T, dist_of_state, activity = "BUS")

pvalues_bus <- c()
for (i in 2:7){
  pvalues_bus <- c(pvalues_bus, ks.test(dists_bus[[1]], dists_bus[[i]])$p.value)
}

pvalues_bus
```


```{r}
dists_eatout <- lapply(sim_list_T, dist_of_state, activity = "EAT_OUT")

pvalues_eatout <- c()
for (i in 2:7){
  pvalues_eatout <- c(pvalues_eatout, ks.test(dists_eatout[[1]], dists_eatout[[i]])$p.value)
}

pvalues_eatout
```

```{r}
dists_edu <- lapply(sim_list_T, dist_of_state, activity = "EDUCATION")

pvalues_edu <- c()
for (i in 2:7){
  pvalues_edu <- c(pvalues_edu, ks.test(dists_edu[[1]], dists_edu[[i]])$p.value)
}

pvalues_edu
```


```{r}
dists_na <- lapply(sim_list_T, dist_of_state, activity = "N/A")

pvalues_na <- c()
for (i in 2:7){
  pvalues_na <- c(pvalues_na, ks.test(dists_na[[1]], dists_na[[i]])$p.value)
}

pvalues_na
```

```{r}
dists_other <- lapply(sim_list_T, dist_of_state, activity = "OTHER")

pvalues_other <- c()
for (i in 2:7){
  pvalues_other <- c(pvalues_other, ks.test(dists_other[[1]], dists_other[[i]])$p.value)
}

pvalues_other
```


```{r}
dists_shop <- lapply(sim_list_T, dist_of_state, activity = "SHOP")

pvalues_shop <- c()
for (i in 2:7){
  pvalues_shop <- c(pvalues_shop, ks.test(dists_shop[[1]], dists_shop[[i]])$p.value)
}

pvalues_shop
```

```{r}
dists_walk <- lapply(sim_list_T, dist_of_state, activity = "WALK")

pvalues_walk <- c()
for (i in 2:7){
  pvalues_walk <- c(pvalues_walk, ks.test(dists_walk[[1]], dists_walk[[i]])$p.value)
}

pvalues_walk

means_walk <- unlist(lapply(dists_walk, mean))
sds_walk <- unlist(lapply(dists_walk, sd))
```




```{r}
# func <- function(state){
#   dists <- lapply(sim_list_T, dist_of_state, activity = state)
#   means_state <- unlist(lapply(dists, mean))
#   sds_state <- unlist(lapply(dists, sd))
#   means <- round(means_state, 2)
#   sds <- round(sds_state, 2)
#   return(rbind(means, sds))
# }
# 
# all_states <- seqstatl(sequences)
# 
# a1 <- func(all_states[1])
# a2 <- func(all_states[2])
# a3 <- func(all_states[3])
# a4 <- func(all_states[4])
# a5 <- func(all_states[5])
# a6 <- func(all_states[6])
# a7 <- func(all_states[7])
# a8 <- func(all_states[8])
# a9 <- func(all_states[9])
# a10 <- func(all_states[10])
# a11 <- func(all_states[11])
# a12 <- func(all_states[12])
# a13 <- func(all_states[13])
# 
# table <- data.frame(rbind(a1, a2, a3, a4, a5, a6, a7, a8, a9, a10, a11, a12, a13))
# table <- cbind(rep(all_states, each = 2), table)
```


```{r}
# counts_work <- lapply(sim_list_T, count_of_state, activity = "WORK")
# means_work <- unlist(lapply(counts_work, mean))
# sds_work <- unlist(lapply(counts_work, sd))
# round(means_work, 2)
# round(sds_work, 2)
# 
# counts_home <- lapply(sim_list_T, count_of_state, activity = "HOME")
# means_home <- unlist(lapply(counts_home, mean)) # sapply
# sds_home <- unlist(lapply(counts_home, sd))
# round(means_home, 2)
# round(sds_home, 2)
# 
# original <- counts_home[[1]]
# 
# round(sd(original[original < 50]), 2)
# 
# counts_car <- lapply(sim_list_T, count_of_state, activity = "CAR")
# means_car <- unlist(lapply(counts_car, mean))
# sds_car <- unlist(lapply(counts_car, sd))
# round(means_car, 2)
# round(sds_car, 2)
# 
# counts_LR <- lapply(sim_list_T, count_of_state, activity = "LEISURE_RECREATION")
# means_LR <- unlist(lapply(counts_LR, mean))
# sds_LR <- unlist(lapply(counts_LR, sd))
# round(means_LR, 2)
# round(sds_LR, 2)
# 
# counts_PB <- lapply(sim_list_T, count_of_state, activity = "PERSONAL_BUSINESS")
# means_PB <- unlist(lapply(counts_PB, mean))
# sds_PB <- unlist(lapply(counts_PB, sd))
# round(means_PB, 2)
round(sds_PB, 2)
```



## 6. Turbulence

```{r}
turbulence <- lapply(sim_list_T, TraMineR::seqST)

pvalues <- c()
for (i in 2:7){
  pvalues <- c(pvalues, ks.test(turbulence[[1]], turbulence[[i]])$p.value)
}

pvalues
```

## 7. Complexity index

```{r}
complexity <- lapply(sim_list_T, TraMineR::seqici)

pvalues <- c()
for (i in 2:7){
  pvalues <- c(pvalues, ks.test(complexity[[1]], complexity[[i]])$p.value)
}

pvalues
```


## 7. BIC/LRT

```{r}
seqCompare(seqdata = sim_list_T[[1]], seqdata2 = sim_list_T[[2]], method = "HAM")

seqCompare(seqdata = sim_list_T[[1]], seqdata2 = sim_list_T[[3]], method = "HAM")

seqCompare(seqdata = sim_list_T[[1]], seqdata2 = sim_list_T[[4]], method = "HAM")

seqCompare(seqdata = sim_list_T[[1]], seqdata2 = sim_list_T[[5]], method = "HAM")

seqCompare(seqdata = sim_list_T[[1]], seqdata2 = sim_list_T[[6]], method = "HAM")

seqCompare(seqdata = sim_list_T[[1]], seqdata2 = sim_list_T[[7]], method = "HAM")
```

